---
title: "Honda et al. (unsubmitted): Machine Learning QSPR for Caco-2 Permeability"
author: "Greg Honda and John Wambaugh"
date: "August 21, 2023"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): Machine Learning QSPR}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

This vignette uses the QSPR model generated in vignette 2 to make a set of 
predictions of apical:basal membrane permeability.

## Overall Manuscript Abstract
Administered equivalent dose (AED) estimation using *in vitro* hazard and high 
throughput toxicokinetics (HTTK) can be improved by refining assumptions 
regarding fraction absorbed ($F_{abs}$) through the intestine, a component of 
oral bioavailability ($F_{bio}$). Although *in vivo* data to inform $F_{abs}$ 
are often unavailable for non-pharmaceuticals, *in vitro* measures of apparent 
permeability ($P_{app}$) using the Caco-2 cell line have been highly correlated 
with $F_{abs}$ when used in *in vitro-in vivo* extrapolation (IVIVE) modeling. 
To address data gaps for non-drug chemicals, bidirectional $P_{app}$ was 
evaluated using the Caco-2 assay for over 400 chemicals. A random forest 
quantitative structure-property relationship (QSPR) model was developed using 
these and peer-reviewed pharmaceutical data. Both Caco-2 data ($R^2$=0.37) and 
the QSPR model ($R^2$=0.3) were better at predicting human bioavailability 
compared to *in vivo* rat data ($R^2$=0.2). The httk-predicted plasma steady 
state concentrations ($C_{ss}$) for IVIVE were updated, leading to modest 
changes for poorly absorbed chemicals. Experimental data were evaluated for 
sources of measurement uncertainty, which was then accounted for using the Monte 
Carlo method. Revised AEDs were subsequently compared with exposure estimates to
evaluate influence on bioactivity:exposure ratios as a surrogate for risk. 
Ultimately, $P_{app}$ incorporation to adjust for $F_{bio}$ in httk modeling 
improves AED estimations used in HT risk prioritization. 

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size and working directory
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/git/Comptox-Caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
```


### Load the relevant libraries
```{r r_setup}

packages <- c("readxl", "httk",
              "data.table","scales","viridis")
sapply(packages, require, character.only=TRUE) #Note, the "character.only" argument is necessary here

```
## Making QSPR Predictions for Membrane Permeability

Read both OPERA predictions and Padel descriptors:
```{r qspr_read_opera_padel_descriptors}
opera <- read.csv(paste0(loc.wd,"/r_data/qspr/trainset-smi_OPERA2.9Pred.csv"))
desc.cols <- rep(TRUE, dim(opera)[2])
colnames(opera)[1] <- "dtxsid"
desc.cols[regexpr("AD_",colnames(opera))!=-1] <- FALSE
desc.cols[regexpr("_predRange",colnames(opera))!=-1] <- FALSE
desc.cols[regexpr("Conf_index",colnames(opera))!=-1] <- FALSE
opera <- subset(opera,!duplicated(opera))
```

### Make a file of SMILES for Caco2 Predictions:
The table httk::chem.physical_and_invitro.data includes the QSAR_READY_SMILES
from the CCD in the column SMILES.desalt. We will use these to get descriptors
needed to predict Caco2 Pab for all the chemicals.
```{r qspr_makenewpredictionccdfile}
  httk.chems <- httk::chem.physical_and_invitro.data[,"DTXSID"]
  tox21.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/Chemical List TOX21SL-2023-05-05.csv"))$DTXSID
  toxcast.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/Chemical List TOXCAST-2023-05-05.csv"))$DTXSID
  pfas1.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/Chemical List EPAPFAS75S1-2023-05-05.csv"))$DTXSID
  pfas2.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/Chemical List EPAPFAS75S2-2023-05-05.csv"))$DTXSID  
  consumer.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/Chemical List EPACONS-2023-05-05.csv"))$DTXSID 
  cvt.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/cvt_test_substances.csv"))$dsstox_substance_id
  new.httk.chems <- read.table(paste0(
    loc.wd,"/r_data/chemical_lists/HTTK-status-all.txt"),header=TRUE)$DTXSID
  apcra.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/APCRA_Chelsea.csv"))$DTXSID 
  nhanes.chems <- as.data.frame(read_excel(paste0(
    loc.wd,"/r_data/chemical_lists/NHANES_finalBloodSerumChems_2023-05-05.xlsx")))$DTXSID
  dawsonpfas.chems <- read.csv(paste0(
    loc.wd,"/r_data/chemical_lists/S3_Dawsonetal_PFAS_HL_101122.csv"))
  # only want ones in domain of applicability:
  dawsonpfas.chems <-length(unique(subset(dawsonpfas.chems,AMAD==1)$DTXSID))
  
 chems.to.predict <- sort(unique(c(httk.chems,
                                   tox21.chems,
                                   toxcast.chems,
                                   pfas1.chems,
                                   pfas2.chems,
                                   consumer.chems,
                                   cvt.chems,
                                   new.httk.chems,
                                   apcra.chems,
                                   nhanes.chems,
                                   dawsonpfas.chems)))
 
 # don't need predictions for chemicals we already had predictions for
 chems.to.predict <- chems.to.predict[!chems.to.predict %in% opera$dtxsid]
 chems.to.predict <- chems.to.predict[!is.na(chems.to.predict)]
 chems.to.predict <- chems.to.predict[regexpr("DTXSID",chems.to.predict)!=-1]
 chems.to.predict <- gsub(
   "https://comptox.epa.gov/dashboard/chemical/details/","",
    chems.to.predict)
 chems.to.predict <- gsub("\\|c:10\t","",chems.to.predict)
 chems.to.predict <- sort(unique(chems.to.predict))
 length(chems.to.predict)

   write.table(chems.to.predict, 
               file=paste0(loc.wd,"/r_data/QSPR/QSPRPredictionDTXIDsforDashboard.txt"),
               row.names=FALSE,
               col.names=FALSE,
               quote=FALSE)
```

```{r qspr_makenewpredictionsmifile}
  CCD <- read.csv(paste0(loc.wd,"/r_data/QSPR/QSPRPredictionsmilesfromCCD.csv"))
  dim(CCD)
  # Get rid of multiple values:
  CCD$QSAR_READY_SMILES <- sapply(CCD[,"QSAR_READY_SMILES"],
                                  function(x) strsplit(x, ",")[[1]][1])
  # Get rid of quotation marks:
  CCD$QSAR_READY_SMILES <- gsub("\"","",CCD$QSAR_READY_SMILES)
  # Get rid of blank SMILES:
  CCD <- subset(CCD, !is.na(QSAR_READY_SMILES))
  CCD <- subset(CCD, DTXSID != "N/A")
  CCD <- subset(CCD, QSAR_READY_SMILES != "N/A")
  dim(CCD)
  # Get rid of duplicate rows:
  CCD <- subset(CCD,!duplicated(CCD))
  dim(CCD)

  write.table(CCD[,c("QSAR_READY_SMILES","DTXSID")],
            col.names=FALSE,sep="\t",
            row.names=FALSE,
            quote = FALSE,
            file=paste0(loc.wd,"/r_data/QSPR/QSPRPrediction.smi"))
```
Reload the final model here in case we're making predictions in a subsequent
session:
```{r qspr_loadoptimalmodel}
load(paste0(loc.wd,"/r_data/QSPR/optimal_model.RData"))
```

### Read both OPERA predictions and Padel descriptors for httk library
```{r qspr_read_newpredictions_opera_padel_descriptors}
httk.desc <- read.csv(paste0(loc.wd,"/r_data/QSPR/QSPRPrediction-smi_OPERA2.9Pred.csv"))
dim(httk.desc)

#for comparing data vs. qspr let's add in all the training/test chemicals:
data.desc <- read.csv(paste0(loc.wd,"/r_data/QSPR/trainset-smi_OPERA2.9Pred.csv"))
httk.desc <- rbind(httk.desc, data.desc)
dim(httk.desc)

httk.desc$MoleculeID <- gsub("\\|c:10\t","",httk.desc$MoleculeID)

# Ionization fractions:
for (i in 1:dim(httk.desc)[1])
{
  out <- calc_ionization(pH=7.4, 
                         pKa_Donor=httk.desc[i,"pKa_a_pred"],
                         pKa_Accept=httk.desc[i,"pKa_b_pred"])
  for (this.col in names(out)) httk.desc[i,this.col] <- out[[this.col]]
}
dim(httk.desc)
httk.ids <- httk.desc[,"MoleculeID"]
httk.desc <- httk.desc[,opt.desc]
dim(httk.desc)
```
Replace NA's with mean of training set:
```{r qspr_replacehttkNAs}
load(paste0(loc.wd,"/r_data/QSPR/trainingdata-meansd.RData"))

for (this.col in opt.desc)
{
  if (is.numeric(train_msd[1,this.col]))
  {
    httk.desc[is.na(httk.desc[,this.col]),this.col] <- train_msd[1,this.col]
  }
}
```

### Aplicability Domain
Use the Roy et al. (2015) method to determine applicability domain:
```{r qspr_royapplicabilitydomain}
httk.Ski <- httk.desc
httk.Ski[] <- NA

# Roy et al. Algorithm Step a:
for (this.col in opt.desc)
{
  httk.Ski[,this.col] <- abs(httk.desc[this.col] - train_msd[1,this.col]) /
    train_msd[2,this.col]
}
# Roy et al. Algorithm Step b (no extreme descriptors):
httk.Si.max.k <- apply(httk.Ski, 1, max)
httk.AD <- rep(NA,length(httk.Si.max.k))
httk.AD[httk.Si.max.k <= 3] <- 1 # Inside applicability domain
# Roy et al. Algorithm Step c (all extreme descriptors:
httk.Si.min.k <- apply(httk.Ski,1,min)
httk.AD[httk.Si.max.k > 3 &
        httk.Si.min.k > 3] <- 0 # Outside applicability domain
# Roy et al. Algorithm Step d (some extreme descriptors):
httk.S.new.k <- apply(httk.Ski, 1, mean) + 1.28*apply(httk.Ski, 1, sd)
httk.AD[httk.Si.max.k > 3 &
        httk.Si.min.k <= 3 &
        httk.S.new.k <= 3] <- 1 # Inside applicability domain
httk.AD[httk.Si.max.k > 3 &
        httk.Si.min.k <= 3 &
        httk.S.new.k > 3] <- 0 # Outside applicability domain
print(paste0(sum(httk.AD)," HTTK chemicals (",
             signif(sum(httk.AD)/length(httk.AD),3)*100,
             "%) are in the Roy et al. (2015) estimated domain o applicability"))
```

### Use optimal model to predict across HTTK library
```{r qspr_makehttkpredictions}
load(paste0(loc.wd,"/r_data/QSPR/qsprbinnumbersummary.RData"))

httk.pred <- predict(classmodopt, httk.desc)
httk.caco2.qspr <- data.frame(DTXSID=httk.ids, 
                              Pab.Class.Pred=httk.pred,
                              Pab.Pred.AD = httk.AD)
httk.caco2.qspr <- merge(httk.caco2.qspr,chem.physical_and_invitro.data[,c("DTXSID","CAS")],by="DTXSID",all.x=TRUE)

for (this.bin in sort(as.character(unique(httk.caco2.qspr$Pab.Class.Pred))))
{
  bin.value <- qspr.summary[paste0("Bin",this.bin),chosen.model]
  bin.value <- gsub(" \\(",",",bin.value)
  bin.value <- gsub(" - ",",",bin.value)
  bin.value <- gsub("\\)","",bin.value)
  httk.caco2.qspr[as.character(httk.caco2.qspr$Pab.Class.Pred)==this.bin,
                  "Pab.Quant.Pred"] <- bin.value
}

save(httk.caco2.qspr,
     file=paste0(loc.wd,"/results_for_paper/httk_qspr_preds.RData")) 
```

```{r Instructions_to_Update_HTTK}
cat("Now copy the following files to httk-dev/datatables/CACO-2:\
  results_for_paper/TableAllCaco2PabData_10e-6cmps.txt\
  results_for_paper/httk_qspr_preds.RData\
  processed/all_gut_data.RData\
Rerun load_package_data_tables.R and rebuild httk.\n")
```