---
title: "Honda et al. (unsubmitted): Comparison of Oral Absorption Predictions to In Vivo Data"
author: "Greg Honda and John Wambaugh"
date: "September 10, 2023"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): In Vivo Evaluation}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

This vignette uses *in vivo* measurements from the scientific literature to 
evaluate various aspects of the models for relating *in vitro* Caco-2 apparent
permeabilities to fraction orally absorbed.

## Overall Manuscript Abstract
Performance of pharmacokinetic models developed using *in vitro-to-in vivo* 
extrapolation (IVIVE) methods may be improved by refining assumptions regarding 
fraction absorbed ($F_{abs}$) through the intestine, a component of oral 
bioavailability ($F_{bio}$). Although *in vivo* measures of Fabs are often 
unavailable for non-pharmaceuticals, *in vitro* measures of apparent 
permeability ($P_{app}$) using the Caco-2 cell line have been highly correlated 
with $F_{abs}$. We measured bidirectional $P_{app}$ for over 400 
non-pharmaceutical chemicals using the Caco-2 assay. A random forest 
quantitative structure-property relationship (QSPR) model was developed using 
these and peer-reviewed pharmaceutical data. Both Caco-2 data ($R^2$=0.37) and 
the QSPR model ($R^2$=0.29) were better at predicting human bioavailability 
compared to *in vivo* rat data ($R^2$=0.23). After incorporation into a high 
throughput toxicokinetics (HTTK) framework for IVIVE, the Caco-2 data were used 
to estimate in vivo administered equivalent dose (AED) for bioactivity assessed 
*in vitro*, The HTTK-predicted plasma steady state concentrations ($C_{ss}$) 
for IVIVE were revised, with modest changes predicted for poorly absorbed 
chemicals. Experimental data were evaluated for sources of measurement 
uncertainty, which were then accounted for using the Monte Carlo method. 
Revised AEDs were subsequently compared with exposure estimates to evaluate 
effects on bioactivity:exposure ratios, a surrogate for risk. Only minor 
changes in the margin between chemical exposure and predicted bioactive doses 
were observed due to the preponderance of highly absorbed chemicals. 

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/git/Comptox-Caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
setwd(loc.wd)
```

### Load the relevant libraries
```{r r_setup}
packages <- c("ggplot2", "scales", "httk", 
              "readxl", "viridis", "ggpubr", "cramer")
sapply(packages, require,character.only=TRUE) #Note, the "character.only" argument is necessary here
```
### Function for labeling on log-scale:
```{r label_logscale}
scientific_10 <- function(x) {                                  
  out <- gsub("1e", "10^", scientific_format()(x))              
  out <- gsub("\\+","",out)                                     
  out <- gsub("10\\^01","10",out)                               
  out <- parse(text=gsub("10\\^00","1",out))                    
}  
```

### Load custom scripts for analysis
```{r load_useful_scripts}
source(paste0(loc.wd,"/r_scripts/Honda_caco2_utilities.R"))
#source('C:/Users/GHONDA/Documents/HTTKOralRoute/gh_ionization_functions.R')
#source("C:/Users/GHONDA/Documents/R homebrew/chemprop_connect/query_dsstox.measchemprop.R")
#source(paste0(loc.wd,"/r_scripts/rf_train.R"))
#source(paste0(loc.wd,"/r_scripts/Honda_caco2_fullmodel.R"))


```

### Plot Configuration
Here we set standard aspects of all plots, like font size.
```{r ggplot_theme}
gtheme <- theme(axis.title = element_text(size=12,color="black",face="bold"),
                axis.text.y = element_text(size=10, color = "black",face="bold"),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 10),
                legend.key.size = unit(10, "points"),
                panel.background = element_rect(fill="white"),
                axis.line = element_line(color="black"),
                axis.ticks.y = element_line(color="black"),
                legend.position = "top",
                axis.line.x=element_line(color="black"),
                axis.ticks.x=element_line(color="black"),
                axis.text.x = element_text(size = 10,face="bold",color="black"),
                plot.title = element_text(hjust=0,size=12,face="bold"))
```

## ANALYSIS

```{r load_pharma_list}
   pharma <- read_excel(
     paste0(loc.wd, "/r_data/chemical_lists/DSSTox_PHRMPEND_20170531.xlsx"))
```
### Lay out the range of predictions
```{r make_prediction_histograms1}
load(file = paste0(loc.wd, "/r_data/processed/MeanChemicalMeasurements.RData"))

caco2.perchem[dtxsid %in% get_cheminfo(info="dtxsid",suppress.messages=TRUE) &
                !is.na(caco2.perchem$mPab),
              c("Fbio.oral","Fabs.oral","Fgut.oral","Fhep.oral", "kgutabs") :=
              calc_fbio.oral(dtxsid=dtxsid,
                               suppress.messages=TRUE),
              by=dtxsid]
   caco2.perchem$Class <- "Other"
   caco2.perchem[caco2.perchem$dtxsid%in%pharma$DSSTox_Substance_Id,"Class"] <-
     "Pharmaceutical"
   save(caco2.perchem, file = paste0(loc.wd, "/r_data/processed/MeanChemicalMeasurements2.RData"))
```

### Create supplemental table with average measurement for each chemical
This table has one row per chemical:
```{r create_supplemental_table_perchemvalues}
load(file = paste0(loc.wd, "/r_data/processed/MeanChemicalMeasurements2.RData")) 

write.table(caco2.perchem[!duplicated(caco2.perchem$dtxsid),c(
                            "compound",
                            "casrn",                 
                            "dtxsid",
                             "mPab",
                             "sdPab",
                             "mPba",
                             "sdPba",
                             "mPab0",
                             "sdPab0",
                             "mPba0",
                             "sdPba0",
                             "mefflux",
                             "sdefflux",
                             "mefflux0",
                             "sdefflux0",
                             "mrec_ab",
                             "mrec_ba",
                             "sdrec_ab",
                             "sdrec_ba",
                             "ntotal_recab",
                             "ntotal_recba",
                             "ntotal",
                             "ntotal_ab",
                             "ntotal_ba",
                             "ntotal_efflux",
                             "ntotal_rab",
                             "ntotal_rba",
                            "Fbio.oral","Fabs.oral","Fgut.oral","Fhep.oral"
                            )],
              row.names=FALSE,
              na="",
              sep=",",
              file = paste0(loc.wd,
                            "/results_for_paper/TableMeanChemicalMeasurements.csv"))
```

```{r make_prediction_histograms2}
  load(file = paste0(loc.wd, "/r_data/processed/MeanChemicalMeasurements2.RData")) 

  FigPredFabsHist <- ggplot(caco2.perchem)+
        geom_histogram(aes(x = Fabs.oral, fill=Class), 
                   color = "black",
                   alpha=0.4,
                 boundary = 0.
                   #, position="identity"
                   ) +
    labs(y = expression(bold("Count")), 
         x = expression(bold("Predicted"~F[abs]))) +
 #   scale_x_log10(labels=scientific_10)+
# First bin from QSPR:
    geom_vline(xintercept =  calc_fabs.oral(parameters=list(Caco2.Pab=0.23)), 
      linetype="dashed", 
      color = "blue", size=1)+
# Second bin from QSPR:
    geom_vline(xintercept =  calc_fabs.oral(parameters=list(Caco2.Pab=2.08)), 
      linetype="dashed", 
      color = "blue", size=1)+
# Third bin from QSPR:
    geom_vline(xintercept =  calc_fabs.oral(parameters=list(Caco2.Pab=20)), 
      linetype="dashed", 
      color = "blue", size=1)+
    theme_bw()+
        scale_fill_viridis(discrete=2)+
    gtheme
print(FigPredFabsHist)

  FigPredFgutHist <- ggplot(caco2.perchem)+
        geom_histogram(aes(x = Fgut.oral, fill=Class), 
                   color = "black",
                   alpha=0.4,
                 boundary = 0.
                   #, position="identity"
                   ) +
    labs(y = expression(bold("Count")), 
         x = expression(bold("Predicted"~F[gut]))) +
    theme_bw()+
        scale_fill_viridis(discrete=2)+
    gtheme
  
  FigPredFhepHist <- ggplot(caco2.perchem)+
        geom_histogram(aes(x = Fhep.oral, fill=Class), 
                   color = "black",
                   alpha=0.4,
                 boundary = 0.
                   #, position="identity"
                   ) +
    labs(y = expression(bold("Count")), 
         x = expression(bold("Predicted"~F[hep]))) +
    theme_bw()+
        scale_fill_viridis(discrete=2)+
    gtheme
  
  FigPredFbioHist <- ggplot(caco2.perchem)+
        geom_histogram(aes(x = Fbio.oral, fill=Class), 
                   color = "black",
                   alpha=0.4,
                 boundary = 0.
                   #, position="identity"
                   ) +
    labs(y = expression(bold("Count")), 
         x = expression(bold("Predicted"~F[bio]))) +
    theme_bw()+
        scale_fill_viridis(discrete=2)+
    gtheme
```

```{r make_prediction_histograms3}
ggarrange(FigPredFabsHist, FigPredFgutHist, 
          FigPredFhepHist, FigPredFbioHist,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom")
tiff(file = paste0(loc.wd, "/results_for_paper/Fig_FbioPredHists.tiff"),
         height = 3*200, width = 3*200, compression = "lzw")
ggarrange(FigPredFabsHist, FigPredFgutHist, 
          FigPredFhepHist, FigPredFbioHist,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom")
dev.off()

Pab <- 10^seq(log10(0.01),log10(20),0.1)
Fabs <- NULL
for (this.Pab in Pab) { Fabs <- c(Fabs,calc_fabs.oral(parameters=list(Caco2.Pab=this.Pab)))}
```


### Comparison of In Vivo Data with Predictions based on In vitro Caco2 Measurements 

```{r caco2_inivtro_data}
caco2.dt <- httk::honda2023.data
dim(caco2.dt)
colnames(caco2.dt)[colnames(caco2.dt)=="dtxsid"] <- "DTXSID"
# Add column holding the QSPR predictons:
caco2.dt <- merge(caco2.dt,honda2023.qspr,by="DTXSID")
caco2.dt <- caco2.dt[!duplicated(caco2.dt),]
dim(caco2.dt)
caco2.dt$Pab.Pred.Med <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][1]))
caco2.dt$Pab.Pred.Low <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][2]))
caco2.dt$Pab.Pred.High <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][3]))
  save(caco2.dt,
       file=paste0(loc.wd, 
                   "/r_data/processed/caco2dt.RData"))
```
### New Qgut Model Parameters:

Set ratio of liver:gut metabolism:
```{r set_liver2gutmetabolism}
LIVER2GUT <- 100
```

Define a rate of intestinal transport to compete with absorption for poorly absorbed chemicals:
```{r set_Qintesttransport} 
  Qintesttransport <- 0.5
```

Load all the parameters needed to make calculations:
```{r permeability_params}
# gut.data; compiled data table of absorption and permeability data 
  load(paste0(loc.wd, "/r_data/processed/all_gut_data.RData")) 

# Out of all the chemicals with measured Fbio (or components) in Kim, Varma
# and Musther, we only want the ones that 1) have in vitro measured Caco-2 or
# 2) have both in vivo Fbio human and in vivo Fbio rat (only for rat-human
# comparison)
  invivo.table <- subset(gut.data, dtxsid %in% subset(
    chem.physical_and_invitro.data, 
                        !is.na(chem.physical_and_invitro.data$Human.Caco2.Pab) |
                        (!is.na(chem.physical_and_invitro.data$Human.Foral) &
                        !is.na(chem.physical_and_invitro.data$Rat.Foral)))$DTXSID)
   
# Basic version for plots:
   save(invivo.table,file=paste0(loc.wd, "/r_data/processed/all_gut_data_invivotable.RData"))
   colnames(invivo.table)[colnames(invivo.table)=="dtxsid"] <- "DTXSID"
   invivo.table <- merge(invivo.table,caco2.dt,by="DTXSID")
   invivo.table <- subset(invivo.table,DTXSID%in% chem.physical_and_invitro.data$DTXSID)
# Annotate chemical class:   
   invivo.table$Class <- "Other"
   invivo.table[invivo.table$DTXSID%in%pharma$DSSTox_Substance_Id,"Class"] <-
     "Pharmaceutical"
# Figure out which chemicals we have sufficient HTTK for to make predictions:
   httk.casrn <- get_cheminfo()
   
   invivo.table[, logP:=chem.physical_and_invitro.data[
     unlist(sapply(invivo.table$DTXSID, function(x) 
       which(x==chem.physical_and_invitro.data$DTXSID))),"logP"]]
   invivo.table[, MW:=chem.physical_and_invitro.data[
     unlist(sapply(invivo.table$DTXSID, function(x) 
       which(x==chem.physical_and_invitro.data$DTXSID))),"MW"]]
   # In Vivo human fraction sysemically bioavailable from oral dose:
   invivo.table[, Fbio_human:=chem.physical_and_invitro.data[
     unlist(sapply(invivo.table$DTXSID, function(x) 
       which(x==chem.physical_and_invitro.data$DTXSID))),"Human.Foral"]]
   # In Vivo rat fraction sysemically bioavailable from oral dose:
   invivo.table[, Fbio_rat:=chem.physical_and_invitro.data[
     unlist(sapply(invivo.table$DTXSID, function(x) 
       which(x==chem.physical_and_invitro.data$DTXSID))),"Rat.Foral"]]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     casrn %in% httk.casrn, 
                   fuph.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Human",
                     suppress.messages = TRUE)$Funbound.plasma,
                   .(casrn)]
        invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     casrn %in% httk.casrn, 
                   fupr.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Rat",
                     suppress.messages = TRUE,
                     default.to.human=TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,cluh_us:=calc_hep_clearance(
                       chem.cas = casrn[1],
                       species = "Human", 
                       restrictive.clearance = FALSE,
                       hepatic.model = "unscaled",
                       suppress.messages = TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   clur_us:=calc_hep_clearance(
                     chem.cas = casrn[1],
                     species = "Rat",
                     restrictive.clearance=FALSE,
                     hepatic.model = "unscaled",
                     suppress.messages = TRUE,
                     default.to.human=TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffpr_us:=calc_hep_bioavailability(
                       species="Rat",
                       chem.cas= casrn,
                     suppress.messages=TRUE
                       #clu=unique(clur_us)
                       ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffph_us:=calc_hep_bioavailability(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(cluh_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2ph := available_rblood2plasma(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2pr := available_rblood2plasma(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      
  invivo.table[,cluh_hep:=cluh_us*70] %>% # L/h for 70 kg human
        .[,cluh_gut:=cluh_hep/LIVER2GUT] %>% # approximate ratio of cyp abundances
        .[,clur_hep:=clur_us*0.25] %>% # L/h for 0.25 kg rat
        .[,clur_gut:=clur_hep/LIVER2GUT] %>% 
        .[,ffph:=ffph_us] %>% 
        .[,ffpr:=ffpr_us]
     save(invivo.table, file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare1.RData")) 
```   
These calculations should match both the manuscript text and the code in calc_oral_bioavailability.R
```{r Caco_permeability_calcs} 
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare1.RData")) 
   invivo.table[,use.pab:=Pab]
   invivo.table[,Pab.Type:="Measured"]
   invivo.table[is.na(use.pab),"Pab.Type"] <- "QSPR"
   invivo.table[is.na(use.pab),use.pab:=Pab.Pred.Med]
   # Yang 2007 for Caco2 pH7.4
   # peff dimensional 10-4 cm/s
   invivo.table[,peffh:=(10^(0.4926*log10(use.pab)-0.1454))] %>% 
   # Wahajudin (2011)
        .[,peffr:=(peffh + 0.1815)/1.039/10] %>% 
   # m2 area intestine -- Yang et al. (2007)
        .[,Asmallintestineh:=0.66] %>% 
        .[,Asmallintestiner:=71/(100^2)] %>%
   # permeability clearance (CLperm) Yang et al. (2007) equation 8:
   # 10^-4 cm / s * m2 * 1000 L / m^3 / 10^4 * 1 m / 100 cm * 3600 s / h = L / h
        .[,CLpermh:=peffh * Asmallintestineh * 1000/10^4/100*3600] %>%
        .[,CLpermr:=peffr * Asmallintestiner * 1000/10^4/100*3600] %>%
   # Yang et al. (2007) value of 18 L/h blood flow to microvilli of intestinal lumen
        .[,Qvillih:=18] %>% 
        .[,Qvillir:=0.65] %>%
   # Qgut "in terms of fundamental parameters" -- Yang et al. (2007) equation 6:
        .[,Qguth:=Qvillih * CLpermh / (Qvillih + CLpermh)] %>% 
        .[,Qgutr:=Qvillir * CLpermr / (Qvillir + CLpermr)] %>%
   # Qgut Model -- Yang et al. (2007) equation 5:
        .[, fgh_qg := Qguth / (Qguth + fuph.adj*cluh_gut) * Qguth /
            (Qguth+Qintesttransport)] %>% 
        .[, fgr_qg := Qgutr / (Qgutr + fupr.adj*clur_gut) * Qguth /
            (Qguth+Qintesttransport)] %>%
   # Mean residence time -- Grandoni et al. (2019):
        .[, MRTh := 199.2] %>% # min
        .[, MRTr := 88.0] %>% # min
   # Small intestine radius:
        .[, Rsih := 1.75] %>% # cm -- Yu et al. (1999)
        .[, Rsir := 0.18] %>% # cm -- Griffin and O’Driscoll (2008)
   # Yu and Amidon (1999) Equation 11:
        .[, fah_darwichh := 1 - 
            (1 + 2 * peffh * MRTh / 7 / Rsih * 60 / 10^4)^-7] %>% 
        .[, fah_darwichr := 1 - 
            (1 + 2 * peffr * MRTr / 7 / Rsir * 60 / 10^4)^-7] %>% 
   #  Yang et al. (2007) Equation 1:
        .[, fbioh := ffph*fgh_qg*fah_darwichh] %>% 
        .[, fbior := ffpr*fgr_qg*fah_darwichr]
   
   save(invivo.table, 
        file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))  
```   

### Add in predictions from ADMet Predictor
```{r load_admet}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

admet <- as.data.frame(read_excel(paste0(loc.wd, 
                                         "/r_data/admet/Chemicals_Caco2_export.xlsx")))
admetids <- as.data.frame(read_excel(paste0(loc.wd, 
                                         "/r_data/admet/GoodPab310forHisham.xlsx")))
admet$DTXSID <- admetids[admet[,"Identifier"],"DTXSID"]
admet$Fgut.ADMet <- signif(as.numeric(admet[,"%Fa_hum-10.0"])/100,5)
admet$Fbio.ADMet <- signif(as.numeric(admet[,"%Fb_hum-10.0"])/100,5)
invivo.table <- merge(invivo.table,
      admet[,c("DTXSID","Fgut.ADMet","Fbio.ADMet")],
      by="DTXSID",
      all.x=TRUE)

save(invivo.table, 
     file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))  
```

### Create supplemental table with all in vivo data and predictions
```{r write_suptable_invivodata}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

write.csv(invivo.table,
          file=paste0(loc.wd,"/results_for_paper/SupTableInVivoDatandPreds.csv"),
          row.names=FALSE,
          na="")
```

### Measured data from Dahlgren et al. (2015)
```{r make_caco_peff_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
      FigCacoPredPeff <- ggplot(invivo.table)+
        geom_point(aes(x = mpeff_lit, y = peffh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred. ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')),
             x = expression(bold("Measured ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')))+
    #    lims(x = c(-2,2), y = c(-2,2)) +
        scale_colour_viridis_d()+
          scale_x_log10()+
        scale_y_log10()+
        gtheme +
        theme(axis.title = element_text(size = 8)) 
print(FigCacoPredPeff)
    ggsave(FigCacoPredPeff, file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredPeff.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Measured data from Kim et al. (2014)
```{r make_Caco_Fbio_kim_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
      FigCacoPredFbioKim <- ggplot(invivo.table)+
        geom_point(aes(y = fbioh, x = kim_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["bio,h"])),
             x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
print(FigCacoPredFbioKim)
    ggsave(FigCacoPredFbioKim, file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredFbioKim.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Measured data collected by Varma et al. (2010)
```{r make_Caco_Fabs_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
FigCacoPredFabs <- ggplot(invivo.table)+
        geom_point(aes(y = fah_darwichh, x = vo_Fa, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["abs,h"])),
             x = expression(bold("Measured")~bolditalic("F"["abs,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme 
print(FigCacoPredFabs)
    ggsave(FigCacoPredFabs, file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredFabs.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Evaluate Caco2 Fgut Prediction using measured data collected by Varma et al. (2010)
```{r make_Caco_Fgut_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  FigCacoPredFgut <- ggplot(invivo.table)+
        geom_point(aes(y = fgh_qg, x = vo_Fg, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["gut,h"])),
             x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigCacoPredFgut)
  ggsave(FigCacoPredFgut, file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Evaluate ADMet Fgut Prediction using measured data collected by Varma et al. (2010)
```{r make_ADMet_Fgut_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  FigADMetPredFgut <- ggplot(invivo.table)+
        geom_point(aes(y = Fgut.ADMet, x = vo_Fg, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("ADMet Pred.")~bolditalic("F"["gut,h"])),
             x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigADMetPredFgut)
  ggsave(FigADMetPredFgut, 
         file = paste0(loc.wd, 
                              "/results_for_paper/FigADMetPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
summary(lm(vo_Fg ~ Fgut.ADMet, data=invivo.table))
```

### Evaluate predicted first-pass hepatic metabolism using measured data collected by Varma et al. (2010) 
ffp=fraction first pass
```{r make_httk_Fhep_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  
  FighttkPredFhep <- ggplot(invivo.table) +
  geom_point(aes(y = ffph, x = vo_Fh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("Pred.")~bolditalic("F"["hep,h"])),
       x = expression(bold("Measured")~bolditalic("F"["hep,h"]))) +
  lims(x = c(0,1), y = c(0,1)) +
  scale_colour_viridis_d() +
  gtheme
  print(FighttkPredFhep)
  ggsave(FighttkPredFhep, file = paste0(loc.wd, "/results_for_paper/Fig_httkPredFhep.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Fbio calculated from measured data
Using first-pass metabolism only (previous httk approach)
```{r make_httk_FhepFbio_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","ffph","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","ffph","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/oldhttk-invivo-compare-fbioall.RData"))

  FigOldhttkPredFbio <- ggplot(invivo.table) +
  geom_point(aes(y = ffph, x = invivo_fbioh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("Pred.")~bolditalic("F"["hep,h"])),
       x = expression(bold("Measured")~bolditalic("F"["bio,h"]))) +
  lims(x = c(0,1), y = c(0,1)) +
  scale_colour_viridis_d() +
  gtheme
  print(FigOldhttkPredFbio)
  ggsave(FigOldhttkPredFbio, 
         file = paste0(loc.wd, "/results_for_paper/Fig_oldhttkPredFbio.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Fbio calculated from measured data collected by Varma et al. (2010)
```{r make_Caco_Fabs_Varma_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  
  FigCacoPredFbioVarma <- ggplot(invivo.table)+
    geom_point(aes(y = fbioh, x = vo_F, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("Caco2 Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigCacoPredFbioVarma)
  ggsave(FigCacoPredFbioVarma, file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredFbioVarma.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Fbio estimated from rats
```{r make_CacoFabsRat_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  FigHumanRatInVivo <- ggplot(invivo.table)+
        geom_jitter(aes(x = Fbio_human, y = Fbio_rat, color=Class, shape=Class), 
                   alpha = 0.55,
                   size=3,
                   width=0.001,height=0.001)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Measured")~bolditalic("F"["bio,r"])),
             x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigHumanRatInVivo)
  ggsave(FigHumanRatInVivo, file = paste0(loc.wd, "/results_for_paper/Fig_HumanRatInVivo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Fbio using both Kim et al. (2014) and Varma et al. (2010)
```{r make_Caco_Fabs_All_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","fbioh","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","fbioh","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/caco2-invivo-compare-fbioall.RData"))

  FigCacoPredFbioAll <- ggplot(fbio.table)+
    geom_point(aes(y = fbioh, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("Caco2 Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigCacoPredFbioAll)
  ggsave(FigCacoPredFbioAll, 
         file = paste0(loc.wd, 
                       "/results_for_paper/Fig_CacoPredFbioAll.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Fbio predicted by ADMet Predictor
```{r make_admet_Fabs_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","Fbio.ADMet","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","Fbio.ADMet","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/admet-invivo-compare-fbioall.RData"))

  FigADMetPredFbio <- ggplot(fbio.table)+
    geom_point(aes(y = Fbio.ADMet, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("ADMet Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigADMetPredFbio)
  ggsave(FigADMetPredFbio, 
         file = paste0(loc.wd, 
                       "/results_for_paper/Fig_ADMetPredFbio.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

### Combine the evalaution figures of the components of Fbio for the paper:
```{r multipanelfigureforpaper}
ggarrange(FigCacoPredPeff, FigCacoPredFabs, FigCacoPredFgut, FighttkPredFhep, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom")
tiff(file = paste0(loc.wd, "/results_for_paper/Fig_CacoPredFbioComponents.tiff"),
         height = 3*200, width = 3*200, compression = "lzw")
ggarrange(FigCacoPredPeff, FigCacoPredFabs, FigCacoPredFgut, FighttkPredFhep, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom"+
          theme_gray(base_size = 18))
dev.off()
```
### QSPR Evaluation:
```{r caco2_qspr_pab_eval_fig}
  load(file=paste0(loc.wd, 
                   "/r_data/processed/caco2dt.RData"))

# Annotate chemical class:   
   caco2.dt$Class <- "Other"
   caco2.dt[caco2.dt$DTXSID%in%pharma$DSSTox_Substance_Id,"Class"] <-
     "Pharmaceutical"
   
      FigQSPRPredPab <- ggplot(caco2.dt)+
        geom_point(aes(x = Pab, y = Pab.Pred.Med, color=Class, shape=Class), 
                   alpha = 0.15,
                   position = position_jitter(w = 0.0, h = 0.1),
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("QSPR Predicted log"["10"])*bolditalic("P"["ab"])~bold('(10'^'-6'~'cm/s)')),
             x = expression(bold("Measured log"["10"])*bolditalic("P"["ab"])~bold('(10'^'-6'~'cm/s)')))+
       # lims(x = c(-5,3), y = c(-5,3)) +
        scale_x_log10()+
        scale_y_log10()+
        scale_colour_viridis_d()+
        gtheme
  print(FigQSPRPredPab)
    ggsave(FigQSPRPredPab, file = paste0(loc.wd, 
                                         "/results_for_paper/Fig_QSPRPredPab.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```


Repeat all the previous figures, but use the QSPR predictions.

We potentially have more chemicals with in vivo values because we are predicting
Caco-2 Papp rather than restricting to those chemicals with measured values.

Load all the parameters needed to make calculations:
```{r qspr_permeability_params}
   load_honda2023(overwrite=TRUE)
   invivo.table <- gut.data
   colnames(invivo.table)[colnames(invivo.table)=="dtxsid"] <- "DTXSID"
   invivo.table <- merge(invivo.table,caco2.dt,by="DTXSID")
   invivo.table <- subset(invivo.table,DTXSID%in% chem.physical_and_invitro.data$DTXSID)
   httk.casrn <- get_cheminfo()
   
   invivo.table[,
                logP:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"logP"]]
   invivo.table[,
                MW:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"MW"]]
   
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     casrn %in% httk.casrn, 
                   fuph.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Human",
                     suppress.messages = TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     casrn %in% httk.casrn, 
                   fupr.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Rat",
                     suppress.messages = TRUE,
                     default.to.human=TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,cluh_us:=calc_hep_clearance(
                       chem.cas = casrn[1],
                       species = "Human",
                       restrictive.clearance=FALSE,
                       hepatic.model = "unscaled",
                       suppress.messages = TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   clur_us:=calc_hep_clearance(
                     chem.cas = casrn[1],
                     species = "Rat",
                     restrictive.clearance=FALSE,
                     hepatic.model = "unscaled",
                     suppress.messages = TRUE,
                     default.to.human=TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffpr_us:=calc_hep_bioavailability(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(clur_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffph_us:=calc_hep_bioavailability(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(cluh_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2ph := available_rblood2plasma(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2pr := available_rblood2plasma(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      
  invivo.table[,cluh_hep:=cluh_us*70] %>% # L/h for 70 kg human
        .[,cluh_gut:=cluh_hep/LIVER2GUT] %>% # approximate ratio of cyp abundances
        .[,clur_hep:=clur_us*0.25] %>% # L/h for 0.25 kg rat
        .[,clur_gut:=clur_hep/LIVER2GUT] %>% 
        .[,ffph:=ffph_us] %>% 
        .[,ffpr:=ffpr_us]
```   
These calculations should match both the manuscript text and the code in calc_oral_bioavailability.R
```{r qspr_permeability_calcs}  

   invivo.table[,use.pab:=Pab.Pred.Med]
   invivo.table[,Pab.Type:="QSPR"]
   # Yang 2007 for Caco2 pH7.4
   # peff dimensional 10-4 cm/s
   invivo.table[,peffh:=(10^(0.4926*log10(use.pab)-0.1454))] %>% 
   # Wahajudin (2011)
        .[,peffr:=(peffh + 0.1815)/1.039/10] %>% 
   # m2 area intestine -- Yang et al. (2007)
        .[,Asmallintestineh:=0.66] %>% 
        .[,Asmallintestiner:=71/(100^2)] %>%
   # permeability clearance (CLperm) Yang et al. (2007) equation 8:
   # 10^-4 cm / s * m2 * 1000 L / m^3 / 10^4 * 1 m / 100 cm * 3600 s / h = L / h
        .[,CLpermh:=peffh * Asmallintestineh * 1000/10^4/100*3600] %>%
        .[,CLpermr:=peffr * Asmallintestiner * 1000/10^4/100*3600] %>%
   # Yang et al. (2007) value of 18 L/h blood flow to microvilli of intestinal lumen
        .[,Qvillih:=18] %>% 
        .[,Qvillir:=0.65] %>%
   # Qgut "in terms of fundamental parameters" -- Yang et al. (2007) equation 6:
        .[,Qguth:=Qvillih * CLpermh / (Qvillih + CLpermh)] %>% 
        .[,Qgutr:=Qvillir * CLpermr / (Qvillir + CLpermr)] %>%
   # Qgut Model -- Yang et al. (2007) equation 5:
        .[, fgh_qg := Qguth / (Qguth + fuph.adj*cluh_gut) * Qguth /
            (Qguth+Qintesttransport)] %>% 
        .[, fgr_qg := Qgutr / (Qgutr + fupr.adj*clur_gut) * Qguth /
            (Qguth+Qintesttransport)] %>%
   # Mean residence time -- Grandoni et al. (2019):
        .[, MRTh := 199.2] %>% # min
        .[, MRTr := 88.0] %>% # min
   # Small intestine radius:
        .[, Rsih := 1.75] %>% # cm -- Yu et al. (1999)
        .[, Rsir := 0.18] %>% # cm -- Griffin and O’Driscoll (2008)
   # Yu and Amidon (1999) Equation 11:
        .[, fah_darwichh := 1 - 
            (1 + 2 * peffh * MRTh / 7 / Rsih * 60 / 10^4)^-7] %>% 
        .[, fah_darwichr := 1 - 
            (1 + 2 * peffr * MRTr / 7 / Rsir * 60 / 10^4)^-7] %>% 
   #  Yang et al. (2007) Equation 1:
        .[, fbioh := ffph*fgh_qg*fah_darwichh] %>% 
        .[, fbior := ffpr*fgr_qg*fah_darwichr]

  save(invivo.table, file=paste0(loc.wd, 
                                 "/r_data/processed/qspr-invivo-compare2.RData"))    
```   
   
```{r make_qspr_peff_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredPeff <- ggplot(invivo.table)+
    geom_point(aes(x = mpeff_lit, y = peffh, color=Class, shape=Class), 
                alpha = 0.75,
                size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')),
         x = expression(bold("Measured ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')))+
    scale_colour_viridis_d()+
    scale_x_log10()+
    scale_y_log10()+
    gtheme +
    theme(axis.title = element_text(size = 8)) 
  print(FigQSPRPredPeff)
  ggsave(FigQSPRPredPeff, file = 
           paste0(loc.wd, "/results_for_paper/Fig_QSPRPredPeff.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
```{r make_QSPR_Fbio_kim_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFbioKim <- ggplot(invivo.table)+
  geom_point(aes(y = fbioh, x = kim_fbioh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
       x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
  lims(x = c(0,1), y = c(0,1))+
  scale_colour_viridis_d()+
  gtheme
  print(FigQSPRPredFbioKim)
  ggsave(FigQSPRPredFbioKim, file = 
           paste0(loc.wd, "/results_for_paper/Fig_QSPRPredFbioKim.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fabs_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFabs <- ggplot(invivo.table) +
    geom_point(aes(y = fah_darwichh, x = vo_Fa, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3) +
    geom_abline(slope = 1, linetype = "dashed") +
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["abs,h"])),
         x = expression(bold("Measured")~bolditalic("F"["abs,h"]))) +
    lims(x = c(0,1), y = c(0,1)) +
    scale_colour_viridis_d() +
    gtheme 

  print(FigQSPRPredFabs)
  ggsave(FigQSPRPredFabs, file = 
           paste0(loc.wd, "/results_for_paper/Fig_QSPRPredFabs.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fgut_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))
  
  FigQSPRPredFgut <- ggplot(invivo.table)+
  geom_point(aes(y = fgh_qg, x = vo_Fg, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3)+
  geom_abline(slope = 1, linetype = "dashed")+
  labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["gut,h"])),
       x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
  lims(x = c(0,1), y = c(0,1))+
  scale_colour_viridis_d()+
  gtheme
  print(FigQSPRPredFgut)
  
  ggsave(FigQSPRPredFgut, file = 
           paste0(loc.wd, "/results_for_paper/Fig_QSPRPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fhep_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFhep <- ggplot(invivo.table)+
    geom_point(aes(y = ffph, x = vo_Fh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3) +
    geom_abline(slope = 1, linetype = "dashed") +
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["hep,h"])),
         x = expression(bold("Measured")~bolditalic("F"["hep,h"]))) +
    lims(x = c(0,1), y = c(0,1)) +
    scale_colour_viridis_d() +
    gtheme
  print(FigQSPRPredFhep)
  ggsave(FigQSPRPredFhep, file = 
           paste0(loc.wd, "/results_for_paper/Fig_QSPRPredFhep.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fbio_Varma_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))
  
  FigQSPRPredFbioVarma <- ggplot(invivo.table)+
    geom_point(aes(y = fbioh, x = vo_F, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigQSPRPredFbioVarma)
  ggsave(FigQSPRPredFbioVarma, 
         file = paste0(loc.wd, 
                       "/results_for_paper/Fig_QSPRPredFbioVarma.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Fbio using both Kim et al. (2014) and Varma et al. (2010)
```{r make_QSPR_Fbio_all_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","fbioh","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","fbioh","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
       file=paste0(loc.wd, 
                   "/r_data/processed/qspr-invivo-compare-fbioall.RData"))

  FigQSPRPredFbioAll <- ggplot(fbio.table)+
    geom_point(aes(y = fbioh, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigQSPRPredFbioAll)
  ggsave(FigQSPRPredFbioAll, file = 
         paste0(loc.wd, "/results_for_paper/Fig_QSPRPredFbioAll.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Evaluation Statistics
We made new versions of "invivo.table" combining the Fbio data from Varma and Kim
and saved them in different RData files
```{r build_eval_table}
evaluations <- data.frame()
evaluations["Peff",c("In Vivo","Predicted","Reference","Data")] <- 
  c("mpeff_lit","peffh","Dahlgren et al. (2015)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fabs",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fa","fah_darwichh","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fgut-QGutModel",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fg","fgh_qg","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fgut-ADMet",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fg","Fgut.ADMet","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fhep",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fh","ffph","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fbio",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","fbioh","Kim et al. (2014)",
    "/r_data/processed/caco2-invivo-compare-fbioall.RData")
evaluations["Fbio-Rat",c("In Vivo","Predicted","Reference","Data")] <- 
  c("Fbio_human","Fbio_rat","Musther et al. (2014), Wambaugh et al. (2018)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fbio-QSPR",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","fbioh","Kim et al. (2014)",
    "/r_data/processed/qspr-invivo-compare-fbioall.RData")
evaluations["Fbio-ADMet",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","Fbio.ADMet","Kim et al. (2014)",
    "/r_data/processed/admet-invivo-compare-fbioall.RData")
evaluations["Fbio-PreviousHTTK",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","ffph","Kim et al. (2014)",
    "/r_data/processed/oldhttk-invivo-compare-fbioall.RData")

save(evaluations, file=paste0(loc.wd,"/r_data/processed/evaltable.RData"))
```

```{r rmse_funcion}
rmse <- function(obs,pred, sigfigs = 2)
{
  SE <- (obs - pred)^2
  MSE <- mean(SE)
  RMSE <- sqrt(MSE)
  
  return(signif(RMSE, sigfigs))
}
```

# Use bootstrapping to establish a confidence interval on R2
```{r do_statistics}
load(paste0(loc.wd,"/r_data/processed/evaltable.RData"))
eval.table <- data.frame()
for (this.evaluation in row.names(evaluations))
{
# Load the relevant invivo.table RData
  load(file=paste0(loc.wd, evaluations[this.evaluation,"Data"]))
# Restrict to only non-NA values:
  invivo.table <- as.data.frame(invivo.table)
  this.data <- subset(invivo.table,
                      !is.na(invivo.table[, evaluations[this.evaluation,"In Vivo"]]) &
                      !is.na(invivo.table[, evaluations[this.evaluation,"Predicted"]]))
  num.chem <- dim(this.data)[1]
  set.seed(1234)
  R2.samples <- NULL
  pvalue.samples <- NULL
  RMSE.samples <- NULL
  RMSE.samples.low <- NULL
  RMSE.samples.high <- NULL
  obs <- this.data[, evaluations[this.evaluation,"In Vivo"]]
  pred <- this.data[, evaluations[this.evaluation,"Predicted"]]
  for (i in 1:10000)
  {
# All samples:
    these.samples <- sample(1:length(obs),length(obs),replace=TRUE)  
    this.obs <- obs[these.samples]
    this.pred <- pred[these.samples]
    this.fit <- lm(obs~pred,data=data.frame(obs=this.obs,pred=this.pred))
    R2.samples[i] <- summary(this.fit)$adj.r.squared
    pvalue.samples[i] <- summary(this.fit)$coefficients[2,4]
    RMSE.samples[i] <- rmse(obs = this.obs, pred=this.pred, sigfigs=3)
# Low samples:
    these.obs <- obs[obs <= 0.9]
    these.pred <- pred[obs <= 0.9]
    these.samples <- sample(1:length(these.obs),length(these.obs),replace=TRUE)  
    this.obs <- these.obs[these.samples]
    this.pred <- these.pred[these.samples]
    RMSE.samples.low[i] <- rmse(obs = this.obs, pred=this.pred, sigfigs=3)
# Low samples:
    these.obs <- obs[obs > 0.9]
    these.pred <- pred[obs > 0.9]
    these.samples <- sample(1:length(these.obs),length(these.obs),replace=TRUE)  
    this.obs <- these.obs[these.samples]
    this.pred <- these.pred[these.samples]
    RMSE.samples.high[i] <- rmse(obs = this.obs, pred=this.pred, sigfigs=3)
  }
  eval.table[this.evaluation,c("N.Chem",
                               "Reference",
                               "R2",
                               "R2.Range",
                               "RMSE",
                               "RMSE.Low",
                               "RMSE.High")] <- c(
    num.chem,
    evaluations[this.evaluation,"Reference"],
    signif(median(R2.samples),2),
    paste(signif(quantile(R2.samples,probs=0.025),2),"-",
          signif(quantile(R2.samples,probs=0.975),2)),
    signif(median(RMSE.samples),2),
    signif(median(RMSE.samples.low),2),
    signif(median(RMSE.samples.high),2)
    )
}
```

```{r display_evaluation_table}
knitr::kable(eval.table, 
             caption = "Evaluation of predictions against in vivo data for Fbio and contributing factors.",
             floating.environment="sidewaystable") 
write.csv(eval.table,file=paste0(loc.wd,"/results_for_paper/Tableinvivoevaluationsummary.csv"))
```