---
title: "Honda et al. (unsubmitted): Analysis and Figure Generation"
author: "Greg Honda"
date: "August 3, 2020"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): Analysis and Figure Generation}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

## Abstract
Apical-to-basolateral (PAB) and basolateral-to-apical (PBA) measurements were made in the Caco-2 assay for 484 environmental and pharmaceutical chemicals. After filtering, 310 chemicals had a useable PAB and 396 had a useable PBA. Replicates (> 30) were measured for the control chemicals Warfarin, Talinolol, and Ranitidine. Measurement uncertainty was high (SD: 0.3 log10 units) for the low permeability control (Ranitidine). Of our measured PAB, > 80% had high PAB (> 10x10-6 cm/s). Our measured PAB were combined with literature values to develop a classification quantitative-structure-property relationship (QSPR) model, with a balanced accuracy of 80% for the test set. Measured PAB were also used to predict in vivo oral bioavailability (Fbio,h)in human for pharmaceuticals, and performed slightly better (R2: -0.03, RMSE: 0.30) than assuming a fixed value for PAB. Additionally, measured PAB were used for prediction of in vivo oral bioavailability in rat, which resulted in improved prediction of maximum concentration (previous R2: 0.32, updated R2: 0.70). Finally, measurement uncertainty was accounted for in estimates of oral-equivalent dose (OED) from ToxCast in vitro assays for a simulated population using a Monte-Carlo method. OED were subsequently compared with exposure estimates, and the influence of different extrapolation assumptions on the bioactivity-to-exposure ratio (BER) was evaluated. Generally, the large measurement uncertainty for low PAB makes the use of Caco-2 data for accurate prediction of point values difficult. However, accounting for uncertainty enables the upper limits for oral bioavailability to be accurately represented in calculation of OED.

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Research Projects/Caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
```

### Load the relevant libraries
```{r r_setup}

packages <- c("ggplot2","hexbin","dplyr","gplots","httk","RColorBrewer",
        "viridis","data.table","magrittr",
        "stringr","gridExtra","stringi","RMySQL","DBI","grid","xlsx","lattice",
        "gtable","ggpubr","randomForest","caret","recipes","quantregForest",
        "tcpl")
sapply(packages, require,character.only=TRUE) #Note, the "character.only" argument is necessary her
```

###
```{r something}
source(paste0(loc.wd,"/r_scripts/Honda_caco2_utilities.R"))
#source('C:/Users/GHONDA/Documents/HTTKOralRoute/gh_ionization_functions.R')
#source("C:/Users/GHONDA/Documents/R homebrew/chemprop_connect/query_dsstox.measchemprop.R")
#source(paste0(loc.wd,"/r_scripts/rf_train.R"))
#source(paste0(loc.wd,"/r_scripts/Honda_caco2_fullmodel.R"))


```

## ANALYSIS


### Data summary for chemical properties
```{r summary}
low_rec_co <- 0.4
high_rec_co <- 2
gtheme <- theme(axis.title = element_text(size=12,color="black",face="bold"),
                axis.text.y = element_text(size=10, color = "black",face="bold"),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 10),
                legend.key.size = unit(10, "points"),
                panel.background = element_rect(fill="white"),
                axis.line = element_line(color="black"),
                axis.ticks.y = element_line(color="black"),
                legend.position = "top",
                axis.line.x=element_line(color="black"),
                axis.ticks.x=element_line(color="black"),
                axis.text.x = element_text(size = 10,face="bold",color="black"),
                plot.title = element_text(hjust=0,size=12,face="bold"))
```
###
```{r histograms}

##### histograms #####
# Raw Data
{ 
  load(paste0(loc.wd,"/r_data/caco2_qc/caco2dt_processed.RData"))
  caco2.QC <- fread(paste0(loc.wd,"/r_data/caco2_qc/caco2dt_line101_short.csv"))
  
  caco2.QC[,1] <- NULL
  
  caco2.dt <- caco2.QC[caco2.dt,on=.(test_article,dtxsid,task_order,file_id)]
  caco2.dt <- copy(caco2.dt)
  caco2.dt[, comment_ab3 := as.character(comment_ab3)] %>% 
    .[!is.na(update_Pab1),Pab1:=update_Pab1] %>% 
    .[!is.na(update_Pab2),Pab2:=update_Pab2] %>% 
    .[!is.na(update_Pab3),Pab3:=update_Pab3] %>% 
    .[!is.na(update_rec_ab1),rec_ab1:=update_rec_ab1] %>% 
    .[!is.na(update_rec_ab2),rec_ab2:=update_rec_ab2] %>% 
    .[!is.na(update_rec_ab3),rec_ab3:=update_rec_ab3] %>% 
    .[!is.na(update_Pba1),Pba1:=update_Pba1] %>% 
    .[!is.na(update_Pba2),Pba2:=update_Pba2] %>% 
    .[!is.na(update_Pba3),Pba3:=update_Pba3] %>% 
    .[!is.na(update_rec_ba1),rec_ba1:=update_rec_ba1] %>% 
    .[!is.na(update_rec_ba2),rec_ba2:=update_rec_ba2] %>% 
    .[!is.na(update_rec_ba3),rec_ba3:=update_rec_ba3] %>% 
    .[comment_ab1=="",comment_ab1:=NA_character_] %>% 
    .[comment_ab2=="",comment_ab2:=NA_character_] %>% 
    .[comment_ab3=="",comment_ab3:=NA_character_] %>%
    .[is.na(comment_ab1) & Pab1_orig=="ND",comment_ab1:="ND"] %>% 
    .[is.na(comment_ab2) & Pab2_orig=="ND",comment_ab2:="ND"] %>% 
    .[is.na(comment_ab3) & Pab3_orig=="ND",comment_ab3:="ND"] %>% 
    .[comment_ba1=="",comment_ba1:=NA_character_] %>% 
    .[comment_ba2=="",comment_ba2:=NA_character_] %>% 
    .[comment_ba3=="",comment_ba3:=NA_character_] %>%
    .[is.na(comment_ba1) & Pba1_orig=="ND",comment_ba1:="ND"] %>% 
    .[is.na(comment_ba2) & Pba2_orig=="ND",comment_ba2:="ND"] %>% 
    .[is.na(comment_ba3) & Pba3_orig=="ND",comment_ba3:="ND"] %>%
    .[Pab1 <= 0, comment_ab1:="ND"] %>% 
    .[Pab2 <= 0, comment_ab2:="ND"] %>% 
    .[Pab3 <= 0, comment_ab3:="ND"] %>% 
    .[Pba1 <= 0, comment_ba1:="ND"] %>% 
    .[Pba2 <= 0, comment_ba2:="ND"] %>% 
    .[Pba3 <= 0, comment_ba3:="ND"] %>% 
    .[Pab1 <= 0, Pab1:=NA_real_] %>% 
    .[Pab2 <= 0, Pab2:=NA_real_] %>% 
    .[Pab3 <= 0, Pab3:=NA_real_] %>% 
    .[Pba1 <= 0, Pba1:=NA_real_] %>% 
    .[Pba2 <= 0, Pba2:= NA_real_] %>% 
    .[Pba3 <= 0, Pba3:= NA_real_] %>% 
    .[!(is.na(comment_ab1)|comment_ab1 %in% c("LOD","low_rec")),Pab1:=as.numeric(NA)] %>% 
    .[is.na(rec_ab1) | rec_ab1 < low_rec_co | rec_ab1 > high_rec_co, Pab1:=as.numeric(NA)] %>% 
    .[is.na(comment_ab1) & rec_ab1 < low_rec_co, comment_ab1:="low_rec"] %>% 
    .[is.na(comment_ab1) & rec_ab1 > high_rec_co, comment_ab1:="high_rec"] %>% 
    .[!(is.na(comment_ab2)|comment_ab2 %in% c("LOD","low_rec")),Pab2:=as.numeric(NA)] %>% 
    .[is.na(rec_ab2) | rec_ab2 < low_rec_co | rec_ab2 > high_rec_co, Pab2:=as.numeric(NA)] %>% 
    .[is.na(comment_ab2) & rec_ab2 < low_rec_co, comment_ab2:="low_rec"] %>% 
    .[is.na(comment_ab2) & rec_ab2 > high_rec_co, comment_ab2:="high_rec"] %>% 
    .[!(is.na(comment_ab3)|comment_ab3 %in% c("LOD","low_rec")),Pab3:=as.numeric(NA)] %>% 
    .[is.na(rec_ab3) | rec_ab3 < low_rec_co | rec_ab3 > high_rec_co, Pab3:=as.numeric(NA)] %>% 
    .[is.na(comment_ab3) & rec_ab3 < low_rec_co, comment_ab3:="low_rec"] %>% 
    .[is.na(comment_ab3) & rec_ab3 > high_rec_co, comment_ab3:="high_rec"] %>% 
    .[!(is.na(comment_ba1)|comment_ba1 %in% c("LOD","low_rec")),Pba1:=as.numeric(NA)] %>% 
    .[is.na(rec_ba1) | rec_ba1 < low_rec_co | rec_ba1 > high_rec_co, Pba1:=as.numeric(NA)] %>% 
    .[is.na(comment_ba1) & rec_ba1 < low_rec_co, comment_ba1:="low_rec"] %>% 
    .[is.na(comment_ba1) & rec_ba1 > high_rec_co, comment_ba1:="high_rec"] %>% 
    .[!(is.na(comment_ba2)|comment_ba2 %in% c("LOD","low_rec")),Pba2:=as.numeric(NA)] %>% 
    .[is.na(rec_ba2) | rec_ba2 < low_rec_co | rec_ba2 > high_rec_co, Pba2:=as.numeric(NA)] %>% 
    .[is.na(comment_ba2) & rec_ba2 < low_rec_co, comment_ba2:="low_rec"] %>% 
    .[is.na(comment_ba2) & rec_ba2 > high_rec_co, comment_ba2:="high_rec"] %>% 
    .[!(is.na(comment_ba3)|comment_ba3 %in% c("LOD","low_rec")),Pba3:=as.numeric(NA)] %>% 
    .[is.na(rec_ba3) | rec_ba3 < low_rec_co | rec_ba3 > high_rec_co, Pba3:=as.numeric(NA)] %>% 
    .[is.na(comment_ba3) & rec_ba3 < low_rec_co, comment_ba3:="low_rec"] %>% 
    .[is.na(comment_ba3) & rec_ba3 > high_rec_co, comment_ba3:="high_rec"]
}

# Filter Caco2.dt
{
  caco2.filt <- copy(caco2.dt)
  caco2.filt[!(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
           rec_ab:=mean(c(rec_ab1,rec_ab2,rec_ab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                                     (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                                     (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(rec_ab1,rec_ab2,rec_ab3)] %>% 
    .[!(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      sd_rec_ab:=sd(c(rec_ab1,rec_ab2,rec_ab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                                 (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                                 (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(rec_ab1,rec_ab2,rec_ab3)] %>% 
    .[!(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      rec_ba:=mean(c(rec_ba1,rec_ba2,rec_ba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                                (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                                (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(rec_ba1,rec_ba2,rec_ba3)] %>% 
    .[!(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      sd_rec_ba:=sd(c(rec_ba1,rec_ba2,rec_ba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                                 (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                                 (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(rec_ba1,rec_ba2,rec_ba3)] %>% 
    .[!(is.na(Pab1)&is.na(Pab2)&is.na(Pab3)) & !(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      Pab_c:=mean(c(Pab1,Pab2,Pab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                      (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                      (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm = T),.(Pab1,Pab2,Pab3)] %>% 
    .[!(is.na(Pab1)&is.na(Pab2)&is.na(Pab3)) & !(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      sd_Pab:=sd(c(Pab1,Pab2,Pab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                     (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                     (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(Pab1,Pab2,Pab3)] %>% 
    .[!(is.na(Pba1)&is.na(Pba2)&is.na(Pba3)) & !(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      Pba_c:=mean(c(Pba1,Pba2,Pba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                      (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                      (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(Pba1,Pba2,Pba3)] %>% 
    .[!(is.na(Pba1)&is.na(Pba2)&is.na(Pba3)) & !(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      sd_Pba := sd(c(Pba1,Pba2,Pba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                       (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                       (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(Pba1,Pba2,Pba3)]
  
  caco2.filt[,Pab:=Pab_c] %>% 
    .[,Pba:=Pba_c]
  caco2.filt[,batch_id:=batch_guess]  
  caco2.filt[casrn=="106-47-8",compound:="4-Chloroaniline"] %>% 
    .[casrn=="33228-44-3",compound:="4-Pentylaniline"]
  caco2.filt[casrn == "66357-35-5", c("compound", "dtxsid") := list("Ranitidine", "DTXSID8045191")] %>% 
    .[casrn == "57460-41-0", c("compound", "dtxsid") := list("Talinolol", "DTXSID6046426")] %>% 
    .[casrn == "81-81-2", c("compound", "dtxsid") := list("Warfarin", "DTXSID5023742")]
  
}

# recovery vs permeability graphs - S1
{

  lmstat1 <- summary(lm(Pab ~ rec_ab, data = caco2.filt))
  lmstat2 <- summary(lm(Pab/rec_ab ~ rec_ab, data = caco2.filt))
  lmstat3 <- summary(lm(Pba ~ rec_ba, data = caco2.filt))
  lmstat4 <- summary(lm(Pba/rec_ba ~ rec_ba, data = caco2.filt))
  
  
  labl.dt1 <- data.table(x = 0.5,
                         y = c(120,100),
                         labl = c("p*'-'*value:~'<'~0.001",
                                  paste0("R^2: ", signif(lmstat1$r.squared,2))))
  labl.dt2 <- data.table(x = 0.5,
                         y = c(120,100),
                         labl = c(paste0("p*'-'*value: ", signif(lmstat2$coefficients[2,4],2)),
                                  paste0("R^2: ", signif(lmstat2$r.squared,2))))
  labl.dt3 <- data.table(x = 0.5,
                         y = c(120,100),
                         labl = c("p*'-'*value:~'<'~0.001",
                                  paste0("R^2: ", signif(lmstat3$r.squared,2))))
  labl.dt4 <- data.table(x = 0.5,
                         y = c(120,100),
                         labl = c(paste0("p*'-'*value: ", signif(lmstat2$coefficients[2,4],2)),
                                  paste0("R^2: ", signif(lmstat4$r.squared,2))))
  
  # getsign <- function(x){
  #   
  #   if(x < 0){
  #     y <- "-"
  #   }else{
  #     y <- "+"
  #   }
  #   return(y)
  # }
  
  g1 <- ggplot(caco2.filt) +
    geom_point(aes(x = rec_ab, y = Pab), 
               fill = "grey90", color = "black",
               size = 3, shape = 16, alpha = 0.5) +
    geom_smooth(aes(x = rec_ab, y = Pab), method = "lm")+
    geom_text(data = labl.dt1,aes(x = x, y=y, label = labl), parse = T, hjust = 0)+
    lims(y= c(0,150))+
    labs(x = expression(bold("Recovery")[bolditalic("AB")]), 
         y = expression(bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("a)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 150,ymax = 150,xmax = 0.4, xmin = 0.4)
  print(g1)
  g2 <- ggplot(caco2.filt) +
    geom_point(aes(x = rec_ab, y = Pab/rec_ab), 
               fill = "grey90", color = "black",
               size = 3, shape = 16, alpha = 0.5) +
    geom_smooth(aes(x = rec_ab, y = Pab/rec_ab), method = "lm")+
    geom_text(data = labl.dt2,aes(x = x, y=y, label = labl), parse = T, hjust = 0)+
    lims(y = c(0,150))+
    labs(x = expression(bold("Recovery")[bolditalic("AB")]), 
         y = expression(bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("a)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 150,ymax = 150,xmax = 0.4, xmin = 0.4)
  g3 <- ggplot(caco2.filt) +
    geom_point(aes(x = rec_ba, y = Pba), 
               fill = "grey90", color = "black",
               size = 3, shape = 16, alpha = 0.5) +
    geom_smooth(aes(x = rec_ba, y = Pba), method = "lm")+
    geom_text(data = labl.dt3,aes(x = x, y=y, label = labl), parse = T, hjust = 0)+
    lims(y= c(0,160))+
    labs(x = expression(bold("Recovery")[bolditalic("BA")]), 
         y = expression(bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("b)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 150,ymax = 150,xmax = 0.4, xmin = 0.4)
  g4 <- ggplot(caco2.filt) +
    geom_point(aes(x = rec_ba, y = Pba/rec_ba), 
               fill = "grey90", color = "black",
               size = 3, shape = 16, alpha = 0.5) +
    geom_smooth(aes(x = rec_ba, y = Pba/rec_ba), method = "lm")+
    geom_text(data = labl.dt4,aes(x = x, y=y, label = labl), parse = T, hjust = 0)+
    lims(y = c(0,160))+
    labs(x = expression(bold("Recovery")[bolditalic("BA")]), 
         y = expression(bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("b)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 150,ymax = 150,xmax = 0.4, xmin = 0.4)
  
  ggsave(g1, file = paste0(loc.wd, "/r_data/results_for_paper/s1a_recab_v_Pab1.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g2, file = paste0(loc.wd, "/r_data/results_for_paper/recab_v_Pab2.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3, file = paste0(loc.wd, "/r_data/results_for_paper/s1b_recba_v_Pba1.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g4, file = paste0(loc.wd, "/r_data/results_for_paper/recba_v_Pba2.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
}



caco2.filt[, Pab0 := Pab] %>% 
  .[, Pba0 := Pba] %>% 
  .[, Pab := Pab/rec_ab] %>% 
  .[, Pba := Pba/rec_ba] %>% 
  .[, efflux0 := Pba0/Pab0] %>% 
  .[, efflux.ratio := Pba/Pab] %>% 
  .[, Pab := log10(Pab)] %>% 
  .[, Pba := log10(Pba)] %>% 
  .[, Pab0 := log10(Pab0)] %>% 
  .[, Pba0 := log10(Pba0)]

# batch control pab vs upper and lower 5th percentiles - S2
{
  names(caco2.filt)
  caco2.5perc <- copy(caco2.filt)
  s2.dt <- caco2.5perc[, hcPab := Pab[casrn == "81-81-2" & t_type == "control"], .(batch_id)] %>% 
    .[, lcPab := Pab[casrn == "66357-35-5" & t_type == "control"], .(batch_id)] %>% 
    .[, Pab95 := quantile(Pab[t_type != "control"], 0.95, na.rm = TRUE), .(batch_id)] %>% 
    .[, Pab05 := quantile(Pab[t_type != "control"], 0.05, na.rm = TRUE), .(batch_id)] %>% 
    .[,.(hcPab, lcPab, Pab95, Pab05, batch_id)] %>% 
    unique(.)
  
  g1 <- ggplot(s2.dt) +
    geom_point(aes(x = hcPab, y = Pab95), 
               fill = "grey90", color = "black",
               size = 3, shape = 16, alpha = 0.5) +
    labs(x = expression(bold("Warfarin log"["10"])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)')), 
         y = expression(bold("95%")~bold("log"["10"])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw()+
    gtheme
  #print(g1)
  ggsave(g1, file = paste0(loc.wd, "/r_data/results_for_paper/S2figure.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
  
}
caco2.perchem <- caco2.filt[,
                            .(mPab = mean(Pab, na.rm = T),
                              sdPab = sd(Pab, na.rm = T),
                              mPba = mean(Pba, na.rm = T),
                              sdPba = sd(Pba, na.rm = T),
                              mPab0 = mean(Pab0, na.rm = T),
                              sdPab0 = sd(Pab0, na.rm = T),
                              mPba0 = mean(Pba0, na.rm = T),
                              sdPba0 = sd(Pba0, na.rm = T),
                              mefflux = mean(log10(efflux.ratio), na.rm = T),
                              sdefflux = sd(log10(efflux.ratio), na.rm = T),
                              mefflux0 = mean(efflux0, na.rm = T),
                              sdefflux0 = sd(efflux0, na.rm = T),
                              mrec_ab = mean(rec_ab, na.rm = T),
                              mrec_ba = mean(rec_ba, na.rm = T),
                              sdrec_ab = sd(rec_ab, na.rm = T),
                              sdrec_ba = sd(rec_ba, na.rm = T),
                              ntotal_recab = sum(!is.na(rec_ab)),
                              ntotal_recba = sum(!is.na(rec_ba)),
                              ntotal = .N,
                              ntotal_ab = sum(!is.na(Pab)),
                              ntotal_ba = sum(!is.na(Pba)),
                              ntotal_efflux = sum(!is.na(log10(efflux.ratio)))),
                            .(casrn, dtxsid, compound)]
```
###
```{r permeability}
# Permeability histograms
{
  labl.dt1 <- data.table(x = -2.5, y = 100,
                      labl = paste0("Total Count: ",
                                    caco2.perchem[,.N,.(x1 = !is.na(mPab))][x1 == TRUE, N])) 
  # Pab chems - 310
  labl.dt2 <- data.table(x = -2.5, y= 100,
                      labl = paste0("Total Count: ",
                                    caco2.perchem[,.N,.(x1 = !is.na(mPba))][x1 == TRUE, N])) # Pba chems - 396
  labl.dt3 <- data.table(x = 1, y = 40,
                        labl = paste0("Total Count: ",
                                      caco2.perchem[,.N,.(x1 = !is.na(mPab) & !is.na(mPba))][x1 == TRUE, N])) # efflux chems - 306
  min(caco2.perchem[,.(mPab,mPba,mPab0,mPba0)], na.rm = T)
  max(caco2.perchem[,.(mPab,mPba,mPab0,mPba0)], na.rm = T)
  
  g1a <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = mPab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1, aes(x=x, y=y, label = labl), hjust = 0)+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-3.5,2.5),
         y = c(0, 140))+
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("a)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 130,ymax = 130,xmax = -3, xmin = -3)
  g1b <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = mPba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2, aes(x=x, y=y, label = labl), hjust = 0)+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-3.5,2.5),
         y = c(0, 140))+
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("b)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 130,ymax = 130,xmax = -3, xmin = -3)
  g1c <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = log10(mefflux)), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3, aes(x=x, y=y, label = labl), hjust = 0)+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    theme_bw()+
    gtheme+
    annotation_custom(grob = text_grob("c)", hjust = 0, size = 12, face = "bold"), 
                      ymin = 70,ymax = 70,xmax = -1.2, xmin = -1.2)
  
  g2a <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = mPab0), fill= "grey80", color = "black")+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-3.5,2.5),
         y = c(0, 140))+
    theme_bw()+
    gtheme
  g2b <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = mPba0), fill= "grey80", color = "black")+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-3.5,2.5),
         y = c(0, 140))+
    theme_bw()+
    gtheme
  g2c <- ggplot(caco2.perchem)+
    geom_histogram(aes(x = log10(mefflux0)), fill= "grey80", color = "black")+
    labs(y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    theme_bw()+
    gtheme


    
  ggsave(g1a, file = paste0(loc.wd, "/r_data/results_for_paper/f2a_mPab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g1b, file = paste0(loc.wd, "/r_data/results_for_paper/f2b_mPba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g1c, file = paste0(loc.wd, "/r_data/results_for_paper/f2c_mefflux_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
  ggsave(g2a, file = paste0(loc.wd, "/r_data/results_for_paper/mPab0_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g2b, file = paste0(loc.wd, "/r_data/results_for_paper/mPba0_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g2c, file = paste0(loc.wd, "/r_data/results_for_paper/mefflux0_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
  min(caco2.filt[casrn == "81-81-2",.(Pab,Pba,Pab0,Pba0)], na.rm = T)
  max(caco2.filt[casrn == "81-81-2",.(Pab,Pba,Pab0,Pba0)], na.rm = T)
  labl.dt1a <- caco2.perchem[casrn == "81-81-2",.(labl = c(paste0("Mean: ",signif(mPab,2)),
                                                            paste0("SD: ", signif(sdPab,2)),
                                                            paste0("Total Count: ", ntotal_ab)),
                                                   x = 0.65,
                                                   y = c(13,11,9))]
  labl.dt1b <- caco2.perchem[casrn == "81-81-2",.(labl = c(paste0("Mean: ",signif(mPba,2)),
                                                          paste0("SD: ", signif(sdPba,2)),
                                                          paste0("Total Count: ", ntotal_ba)),
                                                 x = 0.5,
                                                 y = c(8,7,6))]
  labl.dt1c <- caco2.perchem[casrn == "81-81-2",.(labl = c(paste0("Mean: ",signif(mefflux,2)),
                                                          paste0("SD: ", signif(sdefflux,2)),
                                                          paste0("Total Count: ", ntotal_efflux)),
                                                 x = -1,
                                                 y = c(8,7,6))]
  
  labl.dt1d <- caco2.perchem[casrn == "81-81-2",.(labl = c(paste0("Mean: ",signif(mrec_ab,2)),
                                                              paste0("SD: ", signif(sdrec_ab,2)),
                                                              paste0("Total Count: ", ntotal_recab
                                                              )),
                                                     x = 1.25,
                                                     y = c(7,6,5))]
  labl.dt1e <- caco2.perchem[casrn == "81-81-2",.(labl = c(paste0("Mean: ",signif(mrec_ba,2)),
                                                              paste0("SD: ", signif(sdrec_ba,2)),
                                                              paste0("Total Count: ", ntotal_recba
                                                              )),
                                                     x = 1.25,
                                                     y = c(10,8,6))]
  g3a <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = Pab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1a,aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    scale_x_continuous(breaks = c(1, 1.5, 2),limits = c(0.5,2.5), expand = c(0,0))+
    scale_y_continuous(breaks = c(0, 5, 10, 15))+
    theme_bw()+
    gtheme
  #print(g3a)
  g4a <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = Pab0), fill= "grey80", color = "black")+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-0.5,2.5),y = c(0, 17.5))+
    theme_bw()+
    gtheme
  g3b <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = Pba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1b,aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(0.5,1.75))+
    theme_bw()+
    gtheme
  print(g3b)
  g4b <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = Pba0), fill= "grey80", color = "black")+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-0.5,2.5), y = c(0, 17.5))+
    theme_bw()+
    gtheme
  g3c <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = log10(efflux.ratio)), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1c,aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  g4c <- ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = efflux0), fill= "grey80", color = "black")+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  g3d <- 
    ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = rec_ab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1d, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("AB")])) +
    lims(x = c(0,2.2))+
    theme_bw()+
    gtheme
  g3e <- 
    ggplot(caco2.filt[casrn == "81-81-2",])+
    geom_histogram(aes(x = rec_ba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt1e, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "a) Warfarin",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("BA")])) +
    lims(x = c(0,2.2))+
    theme_bw()+
    gtheme
  
  ggsave(g3a, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_Pab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3b, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_Pba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3c, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_efflux_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3d, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_recab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3e, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_recba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
  # ggsave(g4a, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_Pab0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4b, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_Pba0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4c, file = paste0(loc.wd, "/r_data/results_for_paper/warfarin_efflux0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  
  labl.dt2a <- caco2.perchem[casrn == "57460-41-0",.(labl = c(paste0("Mean: ",signif(mPab,2)),
                                                                 paste0("SD: ", signif(sdPab,2)),
                                                                 paste0("Total Count: ", ntotal_ab)),
                                                   x = -0.75,
                                                   y = c(7.5,6.5,5.5))]
  labl.dt2b <- caco2.perchem[casrn == "57460-41-0",.(labl = c(paste0("Mean: ",signif(mPba,2)),
                                                             paste0("SD: ", signif(sdPba,2)),
                                                             paste0("Total Count: ", ntotal_ba)),
                                                    x = -1,
                                                    y = c(7.5,6.5,5.5))]
  labl.dt2c <- caco2.perchem[casrn == "57460-41-0",.(labl = c(paste0("Mean: ",signif(mefflux,2)),
                                                             paste0("SD: ", signif(sdefflux,2)),
                                                             paste0("Total Count: ", ntotal_efflux)),
                                                    x = 0,
                                                    y = c(7.5,6.5,5.5))]
  labl.dt2d <- caco2.perchem[casrn == "57460-41-0",.(labl = c(paste0("Mean: ",signif(mrec_ab,2)),
                                                              paste0("SD: ", signif(sdrec_ab,2)),
                                                              paste0("Total Count: ", ntotal_recab
                                                              )),
                                                     x = 1.25,
                                                     y = c(10,8,6))]
  labl.dt2e <- caco2.perchem[casrn == "57460-41-0",.(labl = c(paste0("Mean: ",signif(mrec_ba,2)),
                                                              paste0("SD: ", signif(sdrec_ba,2)),
                                                              paste0("Total Count: ", ntotal_recba
                                                              )),
                                                     x = 1.25,
                                                     y = c(10,8,6))]
  g3a <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = Pab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2a, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    scale_y_continuous(breaks = c(0,5,10), limits = c(0,10))+
    scale_x_continuous(breaks = c(-1.5, -1.0, -0.5, 0.0), limits = c(-1.75,0.25), expand = c(0,0))+
    theme_bw()+
    gtheme
  print(g3a)
  g4a <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = Pab0), fill= "grey80", color = "black")+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-2.5,0.5))+
    theme_bw()+
    gtheme
  g3b <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = Pba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2b, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-1,2.5))+
    theme_bw()+
    gtheme
  g4b <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = Pba0), fill= "grey80", color = "black")+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-0.5,2.5))+
    theme_bw()+
    gtheme
  g3c <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = log10(efflux.ratio)), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2c, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  g4c <- ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = efflux0), fill= "grey80", color = "black")+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  g3d <- 
    ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = rec_ab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2d, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("AB")])) +
    lims(x = c(0,2.2))+
    theme_bw()+
    gtheme
  g3e <- 
    ggplot(caco2.filt[casrn == "57460-41-0",])+
    geom_histogram(aes(x = rec_ba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt2e, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "b) Talinolol",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("BA")])) +
    lims(x = c(0,2.2))+
    theme_bw()+
    gtheme
  
  ggsave(g3a, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_Pab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3b, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_Pba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3c, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_efflux_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3d, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_recab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3e, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_recba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
  # ggsave(g4a, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_Pab0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4b, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_Pba0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4c, file = paste0(loc.wd, "/r_data/results_for_paper/Talinolol_efflux0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  
  labl.dt3a <- caco2.perchem[casrn == "66357-35-5",.(labl = c(paste0("Mean: ",signif(mPab,2)),
                                                            paste0("SD: ", signif(sdPab,2)),
                                                            paste0("Total Count: ", ntotal_ab
                                                                   )),
                                                   x = -1.5,
                                                   y = c(8,7,6))]
  labl.dt3b <- caco2.perchem[casrn == "66357-35-5",.(labl = c(paste0("Mean: ",signif(mPba,2)),
                                                             paste0("SD: ", signif(sdPba,2)),
                                                             paste0("Total Count: ", ntotal_ba
                                                             )),
                                                    x = -1,
                                                    y = c(7,6,5))]
  labl.dt3c <- caco2.perchem[casrn == "66357-35-5",.(labl = c(paste0("Mean: ",signif(mefflux,2)),
                                                             paste0("SD: ", signif(sdefflux,2)),
                                                             paste0("Total Count: ", ntotal_efflux
                                                             )),
                                                    x = 0,
                                                    y = c(4,3.5,3))]
  labl.dt3d <- caco2.perchem[casrn == "66357-35-5",.(labl = c(paste0("Mean: ",signif(mrec_ab,2)),
                                                              paste0("SD: ", signif(sdrec_ab,2)),
                                                              paste0("Total Count: ", ntotal_recab
                                                              )),
                                                     x = 1.25,
                                                     y = c(7,6,5))]
  labl.dt3e <- caco2.perchem[casrn == "66357-35-5",.(labl = c(paste0("Mean: ",signif(mrec_ba,2)),
                                                              paste0("SD: ", signif(sdrec_ba,2)),
                                                              paste0("Total Count: ", ntotal_recba
                                                              )),
                                                     x = 1.25,
                                                     y = c(10,8,6))]
  
  g3a <- ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = Pab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3a, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    scale_x_continuous(limits = c(-1.75,0.25), breaks = c(-1.5, -1.0, -0.5, 0.0), expand = c(0,0))+
    scale_y_continuous(breaks = c(0,5,10), labels = c(0,5,10), limits = c(0,10))+
    theme_bw()+
    gtheme
  print(g3a)
  g4a <- ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = Pab0), fill= "grey80", color = "black")+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-2,1))+
    theme_bw()+
    gtheme
  g3b <- ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = Pba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3b, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-1,2))+
    theme_bw()+
    gtheme
  g4b <- ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = Pba0), fill= "grey80", color = "black")+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bolditalic("P"["BA"])~bold('(10'^'-6'~'cm/s)'))) +
    lims(x = c(-1,2))+
    theme_bw()+
    gtheme
  g3c <- 
    ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = log10(efflux.ratio)), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3c, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  g3d <- 
    ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = rec_ab), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3d, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("AB")])) +
    lims(x = c(0,2.2))+
    scale_y_continuous(breaks = c(0,5,10))+
    theme_bw()+
    gtheme
  g3e <- 
    ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = rec_ba), fill= "grey80", color = "black")+
    geom_text(data = labl.dt3e, aes(x = x, y= y, label = labl), hjust = 0)+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("Recovery")[bolditalic("BA")])) +
    lims(x = c(0,2.2))+
    theme_bw()+
    gtheme

  g4c <- ggplot(caco2.filt[casrn == "66357-35-5",])+
    geom_histogram(aes(x = efflux0), fill= "grey80", color = "black")+
    labs(title = "c) Ranitidine",
         y = expression(bold("Count")), 
         x = expression(bold("log"['10'])*bold("Efflux Ratio"))) +
    #lims(x = c(0.75,2.25))+
    theme_bw()+
    gtheme
  
  ggsave(g3a, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_Pab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3b, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_Pba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3c, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_efflux_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3d, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_recab_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  ggsave(g3e, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_recba_histo.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  # 
  # ggsave(g4a, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_Pab0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4b, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_Pba0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  # ggsave(g4c, file = paste0(loc.wd, "/r_data/results_for_paper/Ranitidine_efflux0_histo.tiff"),
  #        height = 3, width = 3, dpi = 600, compression = "lzw")
  
  

  
}

caco2.filt[!is.na(Pab),nrep_pab := .N,.(casrn)]
caco2.dup <- caco2.filt[nrep_pab >= 2,] %>% 
  .[,mPab := mean(Pab, na.rm=TRUE), .(casrn)]
caco2.dup <- unique(caco2.dup[,.(mPab,casrn)])[, .(chemrank = rank(mPab),casrn)][caco2.dup, on = "casrn"]
```
###
```{r replicates}
# duplicate measures
{

  txt.dt <- unique(caco2.dup[casrn %in% c("66357-35-5", "57460-41-0", "81-81-2"),.(compound, casrn, mPab)]) %>% 
    .[, y := mPab] %>% 
    .[, x := c(0.1,1,0.3)] %>% 
    .[, hjust := c(0, 1, 0)]
  

  predint1 <- pred_int(x0 = caco2.dup$Pab, y0 = caco2.dup$mPab, alpha = 0.95)
  g1 <- ggplot(caco2.dup)+
    geom_point(aes(x = Pab, y = mPab), alpha = 0.5)+
    #geom_smooth(aes(x = Pab, y = mPab), method = "lm")+
    geom_abline(slope = 1, linetype = "dashed")+
    geom_ribbon(data = predint1$res.dt, aes(x= xn, ymin = yn2, ymax = yn1), alpha = 0.2, fill = "blue")+
    geom_text(data = txt.dt, aes(x = x, y = y, label = compound, hjust = hjust))+
    labs(y = expression(bold("Mean log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)')), 
         x = expression(bold("log"['10'])*bolditalic("P"["AB"])~bold('(10'^'-6'~'cm/s)'))) +
    theme_bw() +
    gtheme
  
  ggplot(predint1$res.dt)+
    geom_point(aes(x= xn, y = resint), alpha = 0.2, fill = "blue")
  ggsave(g1, file = paste0(loc.wd, "/r_data/results_for_paper/f1_replicates.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
    
    
}
```
###
```{r rawcaco2}
# raw caco2
{
  load(paste0(loc.wd,"/r_data/caco2_qc/caco2dt_processed.RData"))
  caco2.QC <- fread(paste0(loc.wd,"/r_data/caco2_qc/caco2dt_line101_short.csv"))
  low_rec_co <- -Inf
  high_rec_co <- Inf
  caco2.QC[,1] <- NULL
  
  caco2.raw <- caco2.QC[caco2.dt,on=.(test_article,dtxsid,task_order,file_id)]
  caco2.raw <- copy(caco2.raw)
  caco2.raw[, comment_ab3 := as.character(comment_ab3)] %>% 
    .[!is.na(update_Pab1),Pab1:=update_Pab1] %>% 
    .[!is.na(update_Pab2),Pab2:=update_Pab2] %>% 
    .[!is.na(update_Pab3),Pab3:=update_Pab3] %>% 
    .[!is.na(update_rec_ab1),rec_ab1:=update_rec_ab1] %>% 
    .[!is.na(update_rec_ab2),rec_ab2:=update_rec_ab2] %>% 
    .[!is.na(update_rec_ab3),rec_ab3:=update_rec_ab3] %>% 
    .[!is.na(update_Pba1),Pba1:=update_Pba1] %>% 
    .[!is.na(update_Pba2),Pba2:=update_Pba2] %>% 
    .[!is.na(update_Pba3),Pba3:=update_Pba3] %>% 
    .[!is.na(update_rec_ba1),rec_ba1:=update_rec_ba1] %>% 
    .[!is.na(update_rec_ba2),rec_ba2:=update_rec_ba2] %>% 
    .[!is.na(update_rec_ba3),rec_ba3:=update_rec_ba3] %>% 
    .[comment_ab1=="",comment_ab1:=NA_character_] %>% 
    .[comment_ab2=="",comment_ab2:=NA_character_] %>% 
    .[comment_ab3=="",comment_ab3:=NA_character_] %>%
    .[is.na(comment_ab1) & Pab1_orig=="ND",comment_ab1:="ND"] %>% 
    .[is.na(comment_ab2) & Pab2_orig=="ND",comment_ab2:="ND"] %>% 
    .[is.na(comment_ab3) & Pab3_orig=="ND",comment_ab3:="ND"] %>% 
    .[comment_ba1=="",comment_ba1:=NA_character_] %>% 
    .[comment_ba2=="",comment_ba2:=NA_character_] %>% 
    .[comment_ba3=="",comment_ba3:=NA_character_] %>%
    .[is.na(comment_ba1) & Pba1_orig=="ND",comment_ba1:="ND"] %>% 
    .[is.na(comment_ba2) & Pba2_orig=="ND",comment_ba2:="ND"] %>% 
    .[is.na(comment_ba3) & Pba3_orig=="ND",comment_ba3:="ND"] %>%
    .[Pab1 <= 0, comment_ab1:="ND"] %>% 
    .[Pab2 <= 0, comment_ab2:="ND"] %>% 
    .[Pab3 <= 0, comment_ab3:="ND"] %>% 
    .[Pba1 <= 0, comment_ba1:="ND"] %>% 
    .[Pba2 <= 0, comment_ba2:="ND"] %>% 
    .[Pba3 <= 0, comment_ba3:="ND"] %>% 
    .[Pab1 <= 0, Pab1:=NA_real_] %>% 
    .[Pab2 <= 0, Pab2:=NA_real_] %>% 
    .[Pab3 <= 0, Pab3:=NA_real_] %>% 
    .[Pba1 <= 0, Pba1:=NA_real_] %>% 
    .[Pba2 <= 0, Pba2:= NA_real_] %>% 
    .[Pba3 <= 0, Pba3:= NA_real_] %>% 
    .[!(is.na(comment_ab1)|comment_ab1 %in% c("LOD","low_rec")),Pab1:=as.numeric(NA)] %>% 
    .[is.na(rec_ab1) | rec_ab1 < low_rec_co | rec_ab1 > high_rec_co, Pab1:=as.numeric(NA)] %>% 
    .[is.na(comment_ab1) & rec_ab1 < low_rec_co, comment_ab1:="low_rec"] %>% 
    .[is.na(comment_ab1) & rec_ab1 > high_rec_co, comment_ab1:="high_rec"] %>% 
    .[!(is.na(comment_ab2)|comment_ab2 %in% c("LOD","low_rec")),Pab2:=as.numeric(NA)] %>% 
    .[is.na(rec_ab2) | rec_ab2 < low_rec_co | rec_ab2 > high_rec_co, Pab2:=as.numeric(NA)] %>% 
    .[is.na(comment_ab2) & rec_ab2 < low_rec_co, comment_ab2:="low_rec"] %>% 
    .[is.na(comment_ab2) & rec_ab2 > high_rec_co, comment_ab2:="high_rec"] %>% 
    .[!(is.na(comment_ab3)|comment_ab3 %in% c("LOD","low_rec")),Pab3:=as.numeric(NA)] %>% 
    .[is.na(rec_ab3) | rec_ab3 < low_rec_co | rec_ab3 > high_rec_co, Pab3:=as.numeric(NA)] %>% 
    .[is.na(comment_ab3) & rec_ab3 < low_rec_co, comment_ab3:="low_rec"] %>% 
    .[is.na(comment_ab3) & rec_ab3 > high_rec_co, comment_ab3:="high_rec"] %>% 
    .[!(is.na(comment_ba1)|comment_ba1 %in% c("LOD","low_rec")),Pba1:=as.numeric(NA)] %>% 
    .[is.na(rec_ba1) | rec_ba1 < low_rec_co | rec_ba1 > high_rec_co, Pba1:=as.numeric(NA)] %>% 
    .[is.na(comment_ba1) & rec_ba1 < low_rec_co, comment_ba1:="low_rec"] %>% 
    .[is.na(comment_ba1) & rec_ba1 > high_rec_co, comment_ba1:="high_rec"] %>% 
    .[!(is.na(comment_ba2)|comment_ba2 %in% c("LOD","low_rec")),Pba2:=as.numeric(NA)] %>% 
    .[is.na(rec_ba2) | rec_ba2 < low_rec_co | rec_ba2 > high_rec_co, Pba2:=as.numeric(NA)] %>% 
    .[is.na(comment_ba2) & rec_ba2 < low_rec_co, comment_ba2:="low_rec"] %>% 
    .[is.na(comment_ba2) & rec_ba2 > high_rec_co, comment_ba2:="high_rec"] %>% 
    .[!(is.na(comment_ba3)|comment_ba3 %in% c("LOD","low_rec")),Pba3:=as.numeric(NA)] %>% 
    .[is.na(rec_ba3) | rec_ba3 < low_rec_co | rec_ba3 > high_rec_co, Pba3:=as.numeric(NA)] %>% 
    .[is.na(comment_ba3) & rec_ba3 < low_rec_co, comment_ba3:="low_rec"] %>% 
    .[is.na(comment_ba3) & rec_ba3 > high_rec_co, comment_ba3:="high_rec"]

  caco2.raw2 <- copy(caco2.raw)
  caco2.raw2[!(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
             rec_ab:=mean(c(rec_ab1,rec_ab2,rec_ab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                                       (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                                       (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(rec_ab1,rec_ab2,rec_ab3)] %>% 
    .[!(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      sd_rec_ab:=sd(c(rec_ab1,rec_ab2,rec_ab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                                 (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                                 (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(rec_ab1,rec_ab2,rec_ab3)] %>% 
    .[!(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      rec_ba:=mean(c(rec_ba1,rec_ba2,rec_ba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                                (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                                (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(rec_ba1,rec_ba2,rec_ba3)] %>% 
    .[!(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      sd_rec_ba:=sd(c(rec_ba1,rec_ba2,rec_ba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                                 (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                                 (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(rec_ba1,rec_ba2,rec_ba3)] %>% 
    .[!(is.na(Pab1)&is.na(Pab2)&is.na(Pab3)) & !(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      Pab_c:=mean(c(Pab1,Pab2,Pab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                      (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                      (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm = T),.(Pab1,Pab2,Pab3)] %>% 
    .[!(is.na(Pab1)&is.na(Pab2)&is.na(Pab3)) & !(is.na(rec_ab1)&is.na(rec_ab2)&is.na(rec_ab3)),
      sd_Pab:=sd(c(Pab1,Pab2,Pab3)[!is.na(c(rec_ab1,rec_ab2,rec_ab3)) &
                                     (c(rec_ab1,rec_ab2,rec_ab3) >= low_rec_co) &
                                     (c(rec_ab1,rec_ab2,rec_ab3) <= high_rec_co)],na.rm=T),.(Pab1,Pab2,Pab3)] %>% 
    .[!(is.na(Pba1)&is.na(Pba2)&is.na(Pba3)) & !(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      Pba_c:=mean(c(Pba1,Pba2,Pba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                      (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                      (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(Pba1,Pba2,Pba3)] %>% 
    .[!(is.na(Pba1)&is.na(Pba2)&is.na(Pba3)) & !(is.na(rec_ba1)&is.na(rec_ba2)&is.na(rec_ba3)),
      sd_Pba := sd(c(Pba1,Pba2,Pba3)[!is.na(c(rec_ba1,rec_ba2,rec_ba3)) &
                                       (c(rec_ba1,rec_ba2,rec_ba3) >= low_rec_co) &
                                       (c(rec_ba1,rec_ba2,rec_ba3) <= high_rec_co)],na.rm=T),.(Pba1,Pba2,Pba3)]
  
  caco2.raw2[,Pab:=Pab_c] %>% 
    .[,Pba:=Pba_c]
  caco2.raw2[,batch_id:=batch_guess]  
  caco2.raw2[casrn=="106-47-8",compound:="4-Chloroaniline"] %>% 
    .[casrn=="33228-44-3",compound:="4-Pentylaniline"]
  caco2.raw2[casrn == "66357-35-5", c("compound", "dtxsid") := list("Ranitidine", "DTXSID8045191")] %>% 
    .[casrn == "57460-41-0", c("compound", "dtxsid") := list("Talinolol", "DTXSID6046426")] %>% 
    .[casrn == "81-81-2", c("compound", "dtxsid") := list("Warfarin", "DTXSID5023742")]
  
  
}
caco2.raw3 <- copy(caco2.raw2) %>% 
  .[rec_ab < 0, rec_ab := NA_real_] %>% 
  .[rec_ba < 0, rec_ba := NA_real_]
caco2.perchemraw <- caco2.raw3[,
                            .(mPab = mean(Pab, na.rm = T),
                              sdPab = sd(Pab, na.rm = T),
                              mPba = mean(Pba, na.rm = T),
                              sdPba = sd(Pba, na.rm = T),
                              mrec_ab = mean(rec_ab, na.rm = T),
                              mrec_ba = mean(rec_ba, na.rm = T),
                              sdrec_ab = sd(rec_ab, na.rm = T),
                              sdrec_ba = sd(rec_ba, na.rm = T),
                              ntotal = .N,
                              ntotal_ab = sum(!is.na(Pab)),
                              ntotal_ba = sum(!is.na(Pba)),
                              ntotal_rab = sum(!is.na(rec_ab)),
                              ntotal_rba = sum(!is.na(rec_ba))),
                            .(casrn, dtxsid, compound)]


labl.dt1 <- data.table(x = 2, y = c(150, 125, 100),
                       labl = c(paste0("Mean: ", signif(mean(caco2.perchemraw[, mrec_ab], na.rm = T),2)),
                                paste0("SD: ", signif(sd(caco2.perchemraw[, mrec_ab], na.rm = T),2)),
                                paste0("Total Count: ", sum(caco2.perchemraw[, !is.na(mrec_ab) & mrec_ab > 0]))
                                ))
labl.dt2 <- data.table(x = 2, y = c(150, 125, 100),
                       labl = c(paste0("Mean: ", signif(mean(caco2.perchemraw[, mrec_ba], na.rm = T),2)),
                                paste0("SD: ", signif(sd(caco2.perchemraw[, mrec_ba], na.rm = T),2)),
                                paste0("Total Count: ", sum(caco2.perchemraw[, !is.na(mrec_ba) & mrec_ba > 0]))
                       ))

g5a <- 
  ggplot(caco2.perchemraw[mrec_ab > 0,])+
  geom_histogram(aes(x = mrec_ab), fill= "grey80", color = "black")+
  geom_vline(xintercept = 1, linetype = "dashed")+
  geom_text(data = labl.dt1, aes(x = x, y = y, label = labl), hjust = 0)+
  labs(#title = "a)",
    y = expression(bold("Count")), 
    x = expression(bold("Recovery"[bolditalic("AB")]))) +
  #lims(x = c(0,2.1), y = c(0,85))+
  scale_x_continuous(limits = c(0, 5), breaks = c(0,1,2,3,4), expand = c(0,0))+
  scale_y_continuous(limits = c(0,200))+
  theme_bw()+
  gtheme+
  annotation_custom(grob = text_grob("a)", hjust = 0, size = 12, face = "bold"), 
                    ymin = 195,ymax = 195,xmax = 0.1, xmin = 0.1)
g5b <- 
  ggplot(caco2.perchemraw[mrec_ba > 0,])+
  geom_histogram(aes(x = mrec_ba), fill= "grey80", color = "black")+
  geom_vline(xintercept = 1, linetype = "dashed")+
  geom_text(data = labl.dt2, aes(x = x, y = y, label = labl), hjust = 0)+
  labs(#title = "b) Talinolol",
    y = expression(bold("Count")), 
    x = expression(bold("Recovery"[bolditalic("BA")]))) +
  scale_x_continuous(limits = c(0, 5), breaks = c(0,1,2,3,4), expand = c(0,0))+
  scale_y_continuous(limits = c(0,200))+
  #lims(x = c(0,2.1), y = c(0,85))+
  theme_bw()+
  gtheme+
  annotation_custom(grob = text_grob("b)", hjust = 0, size = 12, face = "bold"), 
                    ymin = 195,ymax = 195,xmax = 0.1, xmin = 0.1)

ggsave(g5a, file = paste0(loc.wd, "/r_data/results_for_paper/mrec_ab_histo.tiff"),
       height = 3, width = 3, dpi = 600, compression = "lzw")
ggsave(g5b, file = paste0(loc.wd, "/r_data/results_for_paper/mrec_ba_histo.tiff"),
       height = 3, width = 3, dpi = 600, compression = "lzw")



names(caco2.filt)

caco2.raw2[, Pab.unadj.unfilt := log10(Pab)] %>% 
  .[, Pba.unadj.unfilt := log10(Pba)] %>% 
  .[, efflux.unadj.unfilt := Pba/Pab] %>% 
  .[, rec_ab.unfilt := rec_ab] %>% 
  .[, rec_ba.unfilt := rec_ba]


dim(unique(caco2.raw2[,.(casrn, batch_id, t_type)]))
caco2.publish <- caco2.raw2[,.(casrn, batch_id, t_type,
                               Pab.unadj.unfilt,
                               Pba.unadj.unfilt,
                               efflux.unadj.unfilt,
                               rec_ab.unfilt,
                               rec_ba.unfilt)][caco2.filt, 
                                               on = c("casrn", 
                                                      "batch_id", 
                                                      "t_type")]

caco2.publish[, Pab.unadj := Pab0] %>% 
  .[, Pba.unadj := Pba0] %>% 
  .[, efflux.unadj := efflux0]

setcolorder(caco2.publish,
            c("compound","casrn","dtxsid","batch_id","t_type",
              "Pab", "Pba", "efflux.ratio", "rec_ab", "rec_ba",
              "Pab.unadj", "Pba.unadj", "efflux.unadj",
              "Pab.unadj.unfilt", "Pba.unadj.unfilt", "efflux.unadj.unfilt",
              "rec_ab.unfilt", "rec_ba.unfilt"))
caco2.publish[, casrn := paste0(" ", casrn)]
write.xlsx(caco2.publish, file = paste0(loc.wd, "/r_data/results_for_paper/caco2_data.xlsx"))
save(caco2.publish, file = paste0(loc.wd,"/r_data/processed/our_caco2.RData"))

length(unique(caco2.dt[!is.na(casrn),casrn])) #484
caco2.all <- caco2.raw2[,.(mPab = mean(Pab,na.rm = T),
                           mPba = mean(Pba, na.rm = T)),
                        .(casrn)]
caco2.all[,.N,.(is.na(mPab))] #423
caco2.all[,.N,.(is.na(mPba))] #453
length(unique(caco2.publish[!is.na(Pab), casrn])) # 310
length(unique(caco2.publish[!is.na(Pba), casrn])) # 396
length(unique(caco2.publish[!is.na(Pba) & !is.na(Pab), casrn])) # 302
```
