---
title: "Honda et al. (unsubmitted): Impact of Bioavailability on Risk Prioritization"
author: "Greg Honda and John Wambaugh"
date: "August 21, 2023"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): Risk Prioritization}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

This vignette incorporates the Caco-2 data into estimates of oral 
bioavailability and prioritizes chemical risk based on bioactivity:exposure 
ratio.

## Overall Manuscript Abstract

Performance of pharmacokinetic models developed using *in vitro-to-in vivo* 
extrapolation (IVIVE) methods may be improved by refining assumptions regarding 
fraction absorbed ($F_{abs}$) through the intestine, a component of oral 
bioavailability ($F_{bio}$). Although *in vivo* measures of Fabs are often 
unavailable for non-pharmaceuticals, *in vitro* measures of apparent 
permeability ($P_{app}$) using the Caco-2 cell line have been highly correlated 
with $F_{abs}$. We measured bidirectional $P_{app}$ for over 400 
non-pharmaceutical chemicals using the Caco-2 assay. A random forest 
quantitative structure-property relationship (QSPR) model was developed using 
these and peer-reviewed pharmaceutical data. Both Caco-2 data ($R^2$=0.37) and 
the QSPR model ($R^2$=0.29) were better at predicting human bioavailability 
compared to *in vivo* rat data ($R^2$=0.23). After incorporation into a high 
throughput toxicokinetics (HTTK) framework for IVIVE, the Caco-2 data were used 
to estimate in vivo administered equivalent dose (AED) for bioactivity assessed 
*in vitro*, The HTTK-predicted plasma steady state concentrations ($C_{ss}$) 
for IVIVE were revised, with modest changes predicted for poorly absorbed 
chemicals. Experimental data were evaluated for sources of measurement 
uncertainty, which were then accounted for using the Monte Carlo method. 
Revised AEDs were subsequently compared with exposure estimates to evaluate 
effects on bioactivity:exposure ratios, a surrogate for risk. Only minor 
changes in the margin between chemical exposure and predicted bioactive doses 
were observed due to the preponderance of highly absorbed chemicals. 

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/git/comptox-caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
```

### Load the relevant libraries
```{r r_setup}

packages <- c("ggplot2","dplyr","httk",
        "viridis","data.table","magrittr","readxl",
        "gridExtra","grid","lattice",
        "gtable","ggpubr","scales")
sapply(packages, require, character.only=TRUE, quietly=TRUE) #Note, the "character.only" argument is necessary her
```

### Load custom scripts for analysis
```{r load_useful_scripts}
source(paste0(loc.wd,"/r_scripts/Honda_caco2_utilities.R"))
#source('C:/Users/GHONDA/Documents/HTTKOralRoute/gh_ionization_functions.R')
#source("C:/Users/GHONDA/Documents/R homebrew/chemprop_connect/query_dsstox.measchemprop.R")
#source(paste0(loc.wd,"/r_scripts/rf_train.R"))
#source(paste0(loc.wd,"/r_scripts/Honda_caco2_fullmodel.R"))


```

### Plot Configuration
Here we set standard aspects of all plots, like font size
```{r BERplotsetup}
# make BER plot theme
gtheme <- theme(axis.title = element_text(size=12,color="black",face="bold"),
                axis.text.y = element_text(size=10, color = "black",face="bold"),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 10),
                legend.key.size = unit(10, "points"),
                panel.background = element_rect(fill="white"),
                axis.line = element_line(color="black"),
                strip.background = element_blank(),
                axis.ticks.y = element_line(color="black"),
                legend.position = "top",
                axis.line.x=element_line(color="black"),
                axis.ticks.x=element_line(color="black"),
                axis.text.x = element_text(size = 10,face="bold",color="black"),
                plot.title = element_text(hjust=0,size=12,face="bold"))

legend.dt <- data.table(x = 1:3, y = 1:3, 
                        leg.labl = c("AED","Exposure", "Overlap"), 
                        leg.color = c("purple", "yellow", "orange")) %>% 
  .[, leg.labl := factor(leg.labl, levels = c("AED","Exposure", "Overlap"))]
g1leg <- ggplot(legend.dt)+
  geom_point(aes(x = x, y = y, color = leg.labl))+
  scale_color_manual(labels = c("AED","Exposure", "Overlap"),
                     values = c("purple","yellow","orange"))+
  labs(color = "")+
  theme_bw()+
  gtheme+
  theme(legend.position = "bottom")
gleg <- get_legend(g1leg)
```

### Function for labeling plot tick-marks on log-scale:
```{r label_logscale}
scientific_10 <- function(x) {                                  
  out <- gsub("1e", "10^", scientific_format()(x))              
  out <- gsub("\\+","",out)                                     
  out <- gsub("10\\^01","10",out)                               
  out <- parse(text=gsub("10\\^00","1",out))                    
}  
```

## BER plots
```{r calc_mc_css_options}
# collect httk chems for IVIVE
chem.dt <- as.data.table(chem.physical_and_invitro.data)
temp <- chem.dt[!is.na(DTXSID) &
                  !is.na(logP) &
                  !is.na(MP) &
                  !is.na(Human.Funbound.plasma) &
                  !is.na(Human.Clint),
                .(DTXSID, CAS, Compound, logP, Human.Funbound.plasma, Human.Clint, Human.Caco2.Pab)
                ]
# Which chemicals have measure Caco2
measured.chems <- temp$DTXSID[!is.na(temp$Human.Caco2.Pab)]
length(measured.chems)
load_honda2023()
chem.dt <- as.data.table(chem.physical_and_invitro.data)
temp <- chem.dt[!is.na(DTXSID) &
                  !is.na(logP) &
                  !is.na(MP) &
                  !is.na(Human.Funbound.plasma) &
                  !is.na(Human.Clint),
                .(DTXSID, CAS, Compound, logP, Human.Funbound.plasma, Human.Clint, Human.Caco2.Pab)
                ]
dim(temp)
measplusqspr.chems <- temp$DTXSID[!is.na(temp$Human.Caco2.Pab)]
length(measplusqspr.chems)
for(this.cas in temp[regexpr("<",Human.Clint) == -1 &
                     Human.Clint != "ND" &
                     Human.Funbound.plasma != "NF",CAS]){
  parameters <- parameterize_steadystate(chem.cas = this.cas,
                                         suppress.messages=TRUE)
  temp[CAS == this.cas, adj.fuph := parameters$Funbound.plasma] %>% 
    .[CAS == this.cas, clinth := parameters$Clint]
  
}
use.dt <- temp[!is.na(adj.fuph) & !is.na(clinth), ]
# Restrict to chemcials with either measured or predicted Caco2:
use.dt <- use.dt[DTXSID %in% measplusqspr.chems,]
dim(use.dt)
```
### Calculate css for different IVIVE assumptions
```{r calc_css}
set.seed(6252019)
use.dt[, css_caco2 := .(list(suppressWarnings(calc_mc_css(chem.cas = CAS,
                                         which.quantile = c(0.025,0.05,0.25,0.5,
                                                            0.75,0.95,0.975),
                                         Caco2.options = list(overwrite.invivo = TRUE,
                                                              keepit100 = FALSE),
                                         output.units = "uM",
                                         suppress.messages=TRUE)))),.(CAS)]
set.seed(6252019)
use.dt[, css_fgutabs100 := .(list(suppressWarnings(calc_mc_css(chem.cas = CAS,
                                     which.quantile = c(0.025,0.05,0.25,0.5,
                                                        0.75,0.95,0.975),
                                     Caco2.options = list(overwrite.invivo = TRUE,
                                                          keepit100 = TRUE),
                                     output.units = "uM",
                                         suppress.messages=TRUE)))),.(CAS)] #%>% 
 
save(use.dt, measured.chems, file = paste0(loc.wd, "/r_data/processed/AEDtable.RData"))
```

```{r ber_table}
# load Css values
load(file = paste0(loc.wd, "/r_data/processed/AEDtable.RData"))

# load ToxCast Summary file
load(file = paste0(loc.wd, "/r_data/BER/toxcast_summary_15AUG2019.RData"))

# load httk-seem3 data 
load(file = paste0(loc.wd, "/r_data/BER/seem3_httk_chems_15AUG2019.RData"))

# Merge with Toxcast data and convert q5AC50 to OED (aka AED)
aed.dt <- toxcast.summary[use.dt, on = "CAS"]
aed_caco2 <- aed.dt[, lapply(unlist(css_caco2), 
                                 function(x) q5cnom/x), 
                        .(CAS, DTXSID)][,c("gutabs", "IVIVE") := 
list("bold('Caco-2')~bolditalic('F'['bio'])", "bold('Nominal Conc.')")]

aed_fgutabs100 <- aed.dt[, lapply(unlist(css_fgutabs100), 
                               function(x) q5cnom/x), 
                      .(CAS, DTXSID)][,c("gutabs", "IVIVE") := 
list("bold('100 Percent')~bolditalic('F'['abs/gut'])", "bold('Nominal Conc.')")]

# aed_r3_mcaco2_honda1 <- aed.dt[, lapply(unlist(r1_mcaco2), function(x) q5cfree/x), .(CAS, DTXSID)][,c("gutabs", "IVIVE") := 
#                                                                                                      list("bold('Caco-2')~bolditalic('F'['bio'])", "bold('Free Conc.')")]
# aed_r4_mfabs_honda1 <- aed.dt[, lapply(unlist(r2_mfabs), function(x) q5cfree/x), .(CAS, DTXSID)][,c("gutabs", "IVIVE") := 
#                                                                                                    list("bolditalic('In Vivo')~bolditalic('F'['bio'])", "bold('Free Conc.')")]
aed.full <- rbind(aed_caco2,
                  aed_fgutabs100)#,
                  #aed_r3_mcaco2_honda1,
                  #aed_r4_mfabs_honda1)
setnames(aed.full, 3:9, c("q025", "q05", "q25", "q50", "q75", "q95", "q975"))
aed.full[, gutabs := factor(gutabs, levels = c(
  "bold('100 Percent')~bolditalic('F'['abs/gut'])",
  "bold('Caco-2')~bolditalic('F'['bio'])"))] %>% 
  .[, IVIVE := factor(IVIVE, levels = c(
    "bold('Nominal Conc.')", 
    "bold('Free Conc.')"))]
# Make sure we have HTTK for these chemicals and they are in domain:
aed.full <- subset(aed.full,CAS%in%get_cheminfo())
aed.full2 <- seem.dt[,.(DTXSID = dsstox_substance_id, 
                        seem3, seem3.l95, 
                        seem3.u95)][aed.full, on = "DTXSID"]
aed.full2[, BER:=q95/seem3.u95]
aed.full2[BER<1, cross.ber.min:=q95]
aed.full2[BER<1, cross.ber.max:=seem3.u95]
aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])" & 
          IVIVE == "bold('Nominal Conc.')", r100 := rank(
            aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])" & 
            IVIVE == "bold('Nominal Conc.')","BER"])]
aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])",r100:=
          aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
          "r100"]
          ]
aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])" & 
          IVIVE == "bold('Nominal Conc.')", rcaco := rank(
            aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])" & 
            IVIVE == "bold('Nominal Conc.')","BER"])]
aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])" & 
          IVIVE == "bold('Nominal Conc.')" &
          DTXSID %in% measured.chems, r100meas := rank(
            aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])" & 
            IVIVE == "bold('Nominal Conc.')" &
            DTXSID %in% measured.chems,"BER"])]
aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])",r100meas:=
          aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
          "r100meas"]
          ]
aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])" & 
          IVIVE == "bold('Nominal Conc.')" &
          DTXSID %in% measured.chems, rcacomeas := rank(
            aed.full2[gutabs == "bold('Caco-2')~bolditalic('F'['bio'])" & 
            IVIVE == "bold('Nominal Conc.')" &
            DTXSID %in% measured.chems,"BER"])]
aed.full2[,
          c("Fbio", "Fabs", "Fgut", "Fhep") :=
            calc_fbio.oral(chem.cas=CAS,
            suppress.messages=TRUE),by=CAS]

save(aed.full2,file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
```



### Bioactivty:Exposure Ratio Plots

```{r makehistogram}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
hist.table.fabs <- aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             c("DTXSID","Fabs")]
hist.table.fabs$label <- "Fabs"
colnames(hist.table.fabs)[2] <- "Value"
hist.table.fgut <- aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             c("DTXSID","Fgut")]
hist.table.fgut$label <- "Fgut"
colnames(hist.table.fgut)[2] <- "Value"
hist.table.ber <- aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                            c("DTXSID","BER")]
hist.table.ber$label <- "BER"
colnames(hist.table.ber)[2] <- "Value"
hist.table <- rbind(hist.table.fabs, hist.table.ber)
save(hist.table,file=paste0(loc.wd, "/r_data/processed/BER-histograms.RData"))

print(paste("We are assuming that systemic bioavailability of an oral dose is a function of three processes: first-pass hepatic metabolism (independent of gut permeability), gut absorption, and gut metabolism. HTTK already included first-pass hepatic metabolism either by modeling flow from the gut through the liver before it reaches systemic circulation or by multiplying the absorbed dose by Fhep. Therefore, shifts in the predictions of HTTK will be due to only gut absorption (no longer 100%) and gut metabolism (no longer zero).",
            "For the chemicals where we can calculate BER the median value of Fabs is predicted to be",
            signif(median(hist.table.fabs$Value),3),
            "and the median value of Fgut is",
            signif(median(hist.table.fgut$Value),3),
            ". This means for most chemicals we might expect Fbio to decrease only",
            percent(signif(1 - signif(median(hist.table.fabs$Value),3)*
                      signif(median(hist.table.fgut$Value),3),2)),
      ". This reduction is less than one order of magnitude. Meanwhile the median BER is",
      signif(median(hist.table.ber$Value,na.rm=TRUE),2),"or",
      signif(log10(median(hist.table.ber$Value,na.rm=TRUE)),1),
      "orders of magnitude.",
      "For specific chemicals where Fabs is predicted to be low, the changes will be more pronounced.",
      "Fabs is less than 50% for only",
      sum(hist.table.fabs$Value<0.5),
      "of chemicals where we can estimate BER."))
colnames(hist.table.ber)[2] <- "Value"

FigBERHistogram<-ggplot(hist.table, aes(x=Value, fill=label)) + 
  geom_histogram(alpha=0.25, position="identity") +
  labs(x = expression(bold('F'['abs']*' and Bioactivity:Exposure Ratio')), 
        y = "Number of Chemicals") +
  scale_x_log10(labels=scientific_10,limits=c(10^-3,10^7))+
  scale_y_log10(labels=scientific_10)+
scale_fill_discrete(name="",labels=c(expression('BER','F'['abs'],'F'['gut'])))+
  gtheme+
  scale_colour_viridis_d()
print(FigBERHistogram)
ggsave(FigBERHistogram, 
       file = paste0(loc.wd, "/results_for_paper/Fig_BERhistogram.tiff"), 
       dpi = 600, height = 5, width = 5, compression = "lzw")
```

```{r makerankcomparison}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
rank.table <- aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             c("DTXSID","r100")]
rank.table <- cbind(rank.table, aed.full2[gutabs != "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             "rcaco"])
save(rank.table,file=paste0(loc.wd, "/r_data/processed/ranks.RData"))

FigBERRankCompare<-ggplot(rank.table, aes(x=r100, y=rcaco)) + 
  geom_point(alpha=0.5, size=3) +
  scale_colour_viridis_d()+
  labs(y = expression(bold('BER Rank with F'['bio'])), 
        x = expression(bold('BER Rank with F'['abs']~'== F'['gut']~'== 1')))+
  geom_abline(slope=1,intercept=0,linetype="dashed",color="blue")+
  scale_x_log10() + scale_y_log10() +
  gtheme
print(FigBERRankCompare)
ggsave(FigBERRankCompare, 
       file = paste0(loc.wd, "/results_for_paper/Fig_BERrankcompare.tiff"), 
       dpi = 600, height = 5, width = 5, compression = "lzw")
```
```{r calcmccsscheck}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
css.table <- aed.full2[gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             c("DTXSID","q50","Fgut", "Fabs")]
css.table <- cbind(css.table, aed.full2[gutabs != "bold('100 Percent')~bolditalic('F'['abs/gut'])",
                             "q50"])
colnames(css.table)[5]<-"q50.2"
css.table[,"Fbio.eff"] <- css.table[,"q50"]/css.table[,"q50.2"]
css.table[,"Fgutchange"] <- css.table[,"Fgut"]*css.table[,"Fabs"]
save(css.table,file=paste0(loc.wd, "/r_data/ranks.RData"))

Figcsstest<-ggplot(css.table, aes(x=Fgutchange, y=Fbio.eff)) + 
  geom_point(alpha=0.5, size=3) +
  scale_colour_viridis_d()+
  labs(y = "Fabsgut.eff", 
        x = "Fabsgut")+
 # scale_x_log10() + scale_y_log10() +
  labs(y = expression(bold('Effective F'['gut']~'* F'['abs']~'from Monte Carlo')), 
       x = expression(bold('Actual F'['gut']~'* F'['abs'])))+
  geom_abline(slope=1,intercept=0,color="blue",linetype="dashed")+
  gtheme
print(Figcsstest)
ggsave(Figcsstest, 
       file = paste0(loc.wd, "/results_for_paper/Fig_CssTest.tiff"), 
       dpi = 600, height = 5, width = 5, compression = "lzw")
```


```{r extra_chems}
cat(paste(length(unique(subset(aed.full2,!is.na(BER))$DTXSID)) - 
          length(unique(subset(aed.full2,!is.na(BER) &
                                         DTXSID %in% measured.chems)$DTXSID)),
          "extra chemicals with BER thanks to the QSPR."))
```

```{r makeallchemBERfig}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
g1 <- ggplot(subset(aed.full2,
                    IVIVE=="bold('Nominal Conc.')"))+
  facet_grid(rows= vars(gutabs), labeller = label_parsed) +
  geom_point(aes(y = q95, x = r100), color = "purple") +
  geom_point(aes(y = seem3.u95, x = r100), color = "yellow")+
  geom_linerange(aes(ymin = cross.ber.min, 
                     ymax = cross.ber.max, 
                     x = r100), color = "orange")+
 # geom_text(data = figtxt.dt,
 #           mapping = aes(x = x1, y = y1, label = labl1),
#            hjust = 0, parse = FALSE) +
 # geom_text(data = figtxt.dt,
##            mapping = aes(x = x2, y = y2, label = labl2),
 #           hjust = 0, parse = TRUE)+
  labs(x = "Bioactivity:Exposure Ratio", 
       y = expression(bold('log'['10']*'(mg/kgBW/day)')))+
  theme_bw()+
  xlim(1,500)+
  scale_y_log10(limits=c(10^-8,10^2),labels=scientific_10)+
  gtheme
hlay <- t(t(c(rep(1,8),2)))
g2 <- marrangeGrob(grobs = list(g1, gleg), nrow = 2, ncol = 1, top = NULL, layout_matrix = hlay)
print(g2)
ggsave(g2, 
       file = paste0(loc.wd,
                       "/results_for_paper/Fig_BERrankzoom.tiff"),
       dpi = 600, height = 5, width = 7.5, compression = "lzw")
```

```{r makemeasurecacoBERfig}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
# load Css values
load(file = paste0(loc.wd, "/r_data/processed/AEDtable.RData"))

FigBERmeas <- ggplot(subset(aed.full2,DTXSID%in%measured.chems &
                    !is.na(q95) &
                    gutabs != "bold('100 Percent')~bolditalic('F'['abs/gut'])"))+
    geom_linerange(aes(ymin = seem3.u95, 
                     ymax = q95, 
                     x = rcacomeas), color = "grey")+
  geom_linerange(aes(ymin = cross.ber.min, 
                     ymax = cross.ber.max, 
                     x = rcacomeas), color = "orange")+
    geom_point(aes(y = q95, x = rcacomeas), color = "purple") +
  geom_point(aes(y = seem3.u95, x = rcacomeas), color = "yellow")+

  labs(x = "Bioactivity:Exposure Ratio", 
       y = 'mg/kg BW/day')+
  theme_bw()+
 # xlim(1,500)+
  scale_y_log10(limits=c(10^-8,10^2),labels=scientific_10)+
  gtheme
hlay <- t(t(c(rep(1,8),2)))
FigBERleg <- marrangeGrob(grobs = list(FigBERmeas, gleg), nrow = 2, ncol = 1, top = NULL, layout_matrix = hlay)
print(FigBERleg)
ggsave(FigBERleg, 
       file = paste0(loc.wd,
                       "/results_for_paper/Fig_BERrankmeascaco2.tiff"),
       dpi = 600, height = 5, width = 7.5, compression = "lzw")
```

```{r makemeasurecacoBERfig2}
load(file=paste0(loc.wd, "/r_data/processed/BERtable.RData"))
FigBERall <- ggplot(subset(aed.full2,
                    !is.na(q95) &
                    gutabs != "bold('100 Percent')~bolditalic('F'['abs/gut'])"))+
    geom_linerange(aes(ymin = seem3.u95, 
                     ymax = q95, 
                     x = rcaco), color = "grey")+
  geom_linerange(aes(ymin = cross.ber.min, 
                     ymax = cross.ber.max, 
                     x = rcaco), color = "orange")+
    geom_point(aes(y = q95, x = rcaco), color = "purple") +
  geom_point(aes(y = seem3.u95, x = rcaco), color = "yellow")+

  labs(x = "Bioactivity:Exposure Ratio", 
       y = 'mg/kg BW/day')+
  theme_bw()+
  scale_y_log10(limits=c(10^-8,10^2),labels=scientific_10)+
  gtheme
hlay <- t(t(c(rep(1,8),2)))
FigBERleg <- marrangeGrob(grobs = list(FigBERall, gleg), nrow = 2, ncol = 1, top = NULL, layout_matrix = hlay)
print(FigBERleg)
ggsave(FigBERleg, 
       file = paste0(loc.wd,
                       "/results_for_paper/Fig_BERrankallcaco2.tiff"),
       dpi = 600, height = 5, width = 7.5, compression = "lzw")
```
```{r multipanelBER}
ggarrange(FigBERmeas, FigBERall, 
          labels = c("A", "B"),
          ncol = 1, nrow = 2,
          common.legend = TRUE, legend = "bottom")
tiff(file = paste0(loc.wd, "/results_for_paper/Fig_BERTwoPanel.tiff"),
         height = 3*200, width = 3*200, compression = "lzw")
ggarrange(FigBERmeas, FigBERall, 
          labels = c("A", "B"),
          ncol = 1, nrow = 2,
          common.legend = TRUE, legend = "bottom"+
          theme_gray(base_size = 18))
dev.off()
```
### Identify the poorly absorbed chemicals:
```{r lowfabstable}
low.fabs <- subset(aed.full2,Fabs<0.5)
low.fabs.table <- subset(low.fabs,gutabs == "bold('100 Percent')~bolditalic('F'['abs/gut'])")
low.fabs.table<- low.fabs.table[,c("DTXSID","CAS","Fabs","Fgut","Fhep","Fbio","seem3.u95","q95","BER")]
low.fabs.table <- low.fabs.table[,q952:=
                        subset(low.fabs,gutabs != 
                                 "bold('100 Percent')~bolditalic('F'['abs/gut'])")$q95]
low.fabs.table <- low.fabs.table[,BER2:=
                        subset(low.fabs,gutabs != 
                                 "bold('100 Percent')~bolditalic('F'['abs/gut'])")$BER]
colnames(low.fabs.table)[colnames(low.fabs.table)=="seem3.u95"]<-"SEEM3"
colnames(low.fabs.table)[colnames(low.fabs.table)=="q95"]<-"ToxCast AED Fabs=Fgut=1"
colnames(low.fabs.table)[colnames(low.fabs.table)=="BER"]<-"BER Fabs=Fgut=1"
colnames(low.fabs.table)[colnames(low.fabs.table)=="q952"]<-"ToxCast AED Caco2"
colnames(low.fabs.table)[colnames(low.fabs.table)=="BER2"]<-"BER Caco2"
low.fabs.table <- as.data.frame(low.fabs.table)
for (i in 3:11) low.fabs.table[,i] <- signif(low.fabs.table[,i],3)
low.fabs.table <- low.fabs.table[order(low.fabs.table$Fbio),]
knitr::kable(low.fabs.table, 
             caption = "Chemicals with Low Caco2-Predicted Fabs (Poorly absorbed chemicals)",
             floating.environment="sidewaystable") 
write.csv(low.fabs.table,file=paste0(loc.wd,"/results_for_paper/Tablepoorlyabsorbedchemicals.csv"))
```