---
title: "Honda et al. (unsubmitted): Comparison of Oral Absorption Predictions to In Vivo Data"
author: "Greg Honda and John Wambaugh"
date: "September 10, 2023"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): In Vivo Evaluation}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

## Abstract
Administered equivalent dose (AED) estimation using in vitro hazard and high throughput toxicokinetics (HTTK) can be improved by refining assumptions regarding fraction absorbed (Fabs) through the intestine, a component of oral bioavailability (Fbio). Although in vivo data to inform Fabs are often unavailable for non-pharmaceuticals, in vitro measures of apparent permeability (Papp) using the Caco-2 cell line have been highly correlated with Fabs when used in in vitro-in vivo extrapolation (IVIVE) modeling. To address data gaps for non-drug chemicals, bidirectional Papp was evaluated using the Caco-2 assay for over 400 chemicals. A random forest quantitative structure-property relationship (QSPR) model was developed using these and peer-reviewed pharmaceutical data. Both Caco-2 data (R2=0.35) and the QSPR model (R2=0.27) were better at predicting human bioavailability compared to in vivo rat data (R2=0.18). The httk-predicted plasma steady state concentrations (Css) for IVIVE were updated, leading to modest changes for poorly absorbed chemicals. Experimental data were evaluated for sources of measurement uncertainty, which was then accounted for using the Monte Carlo method. Revised AEDs were subsequently compared with exposure estimates to evaluate influence on bioactivity:exposure ratios as a surrogate for risk. Ultimately, Papp incorporation to adjust for Fbio in httk modeling improves AED estimations used in HT risk prioritization. 

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/git/comptox-caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
```

### Load the relevant libraries
```{r r_setup}

packages <- c("ggplot2","hexbin","dplyr","gplots","httk","RColorBrewer",
        "viridis","data.table","magrittr","readxl",
        "stringr","gridExtra","stringi","RMySQL","DBI","grid","xlsx","lattice",
        "gtable","ggpubr","randomForest","caret","recipes","quantregForest",
        "tcpl","scales")
sapply(packages, require,character.only=TRUE) #Note, the "character.only" argument is necessary her
```

### Load custom scripts for analysis
```{r load_useful_scripts}
source(paste0(loc.wd,"/r_scripts/Honda_caco2_utilities.R"))
#source('C:/Users/GHONDA/Documents/HTTKOralRoute/gh_ionization_functions.R')
#source("C:/Users/GHONDA/Documents/R homebrew/chemprop_connect/query_dsstox.measchemprop.R")
#source(paste0(loc.wd,"/r_scripts/rf_train.R"))
#source(paste0(loc.wd,"/r_scripts/Honda_caco2_fullmodel.R"))


```

## ANALYSIS

Configure figure theme
```{r summary}
low_rec_co <- 0.4
high_rec_co <- 2
gtheme <- theme(axis.title = element_text(size=12,color="black",face="bold"),
                axis.text.y = element_text(size=10, color = "black",face="bold"),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 10),
                legend.key.size = unit(10, "points"),
                panel.background = element_rect(fill="white"),
                axis.line = element_line(color="black"),
                axis.ticks.y = element_line(color="black"),
                legend.position = "top",
                axis.line.x=element_line(color="black"),
                axis.ticks.x=element_line(color="black"),
                axis.text.x = element_text(size = 10,face="bold",color="black"),
                plot.title = element_text(hjust=0,size=12,face="bold"))
```

### Comparison of In Vivo Data with Predictions based on In vitro Caco2 Measurements 

```{r caco2_inivtro_data}
caco2.dt <- httk::honda2023.data
dim(caco2.dt)
colnames(caco2.dt)[colnames(caco2.dt)=="dtxsid"] <- "DTXSID"
# Add column holding the QSPR predictons:
caco2.dt <- merge(caco2.dt,honda2023.qspr,by="DTXSID")
caco2.dt <- caco2.dt[!duplicated(caco2.dt),]
dim(caco2.dt)
caco2.dt$Pab.Pred.Med <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][1]))
caco2.dt$Pab.Pred.Low <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][2]))
caco2.dt$Pab.Pred.High <- sapply(caco2.dt$Pab.Quant.Pred,function(x) as.numeric(strsplit(x,",")[[1]][3]))
  save(caco2.dt,
       file=paste0(loc.wd, 
                   "/r_data/processed/caco2dt.RData"))
```

Load all the parameters needed to make calculations:
```{r permeability_params}
# gut.data; compiled data table of absorption and permeability data 
   load(paste0(loc.wd, "/r_data/processed/all_gut_data_25MAR2019.RData")) 
   pharma <- read_excel(
     paste0(loc.wd, "/r_data/chemical_lists/DSSTox_PHRMPEND_20170531.xlsx"))
   
   invivo.table <- gut.data
# Basiv version for plots:
   save(invivo.table,file=paste0(loc.wd, "/r_data/processed/all_gut_data_invivotable.RData"))
   colnames(invivo.table)[colnames(invivo.table)=="dtxsid"] <- "DTXSID"
   invivo.table <- merge(invivo.table,caco2.dt,by="DTXSID")
   invivo.table <- subset(invivo.table,DTXSID%in% chem.physical_and_invitro.data$DTXSID)
# Annotate chemical class:   
   invivo.table$Class <- "Other"
   invivo.table[invivo.table$DTXSID%in%pharma$DSSTox_Substance_Id,"Class"] <-
     "Pharmaceutical"
# Figure out which chemicals we have sufficient HTTK for to make predictions:
   httk.casrn <- get_cheminfo()
   
   invivo.table[,logP:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"logP"]]
   invivo.table[,MW:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"MW"]]
   
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     casrn %in% httk.casrn, 
                   fuph.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Human",
                     suppress.messages = TRUE)$Funbound.plasma,
                   .(casrn)]
        invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     casrn %in% httk.casrn, 
                   fupr.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Rat",
                     suppress.messages = TRUE,
                     default.to.human=TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,cluh_us:=calc_hep_clearance(
                       chem.cas = casrn[1],
                       species = "Human", 
                       hepatic.model = "unscaled",
                       suppress.messages = TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   clur_us:=calc_hep_clearance(
                     chem.cas = casrn[1],
                     species = "Rat", 
                     hepatic.model = "unscaled",
                     suppress.messages = TRUE,default.to.human=TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffpr_us:=calc_hep_bioavailability(
                       species="Rat",
                       chem.cas= casrn,
                     suppress.messages=TRUE
                       #clu=unique(clur_us)
                       ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffph_us:=calc_hep_bioavailability(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(cluh_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2ph := available_rblood2plasma(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2pr := available_rblood2plasma(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      
  invivo.table[,cluh_hep:=cluh_us*70] %>% # L/h for 70 kg human
        .[,cluh_gut:=cluh_hep/100] %>% # approximate ratio of cyp abundances
        .[,clur_hep:=clur_us*0.25] %>% # L/h for 0.25 kg rat
        .[,clur_gut:=clur_hep/100] %>% 
        .[,ffph:=ffph_us] %>% 
        .[,ffpr:=ffpr_us]
     save(invivo.table, file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare1.RData")) 
```   
These calculations should match both the manuscript text and the code in calc_oral_bioavailability.R
```{r Caco_permeability_calcs} 
# Define a rate of intestinal transport to compete with absorption for poorly
# absorbed chemicals:
Qintesttransport <- 0.5

    load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare1.RData")) 
   invivo.table[,use.pab:=Pab]
   invivo.table[,Pab.Type:="Measured"]
   invivo.table[is.na(use.pab),"Pab.Type"] <- "QSPR"
   invivo.table[is.na(use.pab),use.pab:=Pab.Pred.Med]
   # Yang 2007 for Caco2 pH7.4
   # peff dimensional 10-4 cm/s
   invivo.table[,peffh:=(10^(0.4926*log10(use.pab)-0.1454))] %>% 
   # Fagerholm 1996
        .[,peffr:=peffh/3.6] %>% 
   # m2 area intestine -- Yang et al. (2007)
        .[,Asmallintestineh:=0.66] %>% 
        .[,Asmallintestiner:=71/(100^2)] %>%
   # permeability clearance (CLperm) Yang et al. (2007) equation 8:
   # 10^-4 cm / s * m2 * 1000 L / m^3 / 10^4 * 1 m / 100 cm * 3600 s / h = L / h
        .[,CLpermh:=peffh * Asmallintestineh * 1000/10^4/100*3600] %>%
        .[,CLpermr:=peffr * Asmallintestiner * 1000/10^4/100*3600] %>%
   # Yang et al. (2007) value of 18 L/h blood flow to microvilli of intestinal lumen
        .[,Qvillih:=18] %>% 
        .[,Qvillir:=0.65] %>%
   # Qgut "in terms of fundamental parameters" -- Yang et al. (2007) equation 6:
        .[,Qguth:=Qvillih * CLpermh / (Qvillih + CLpermh)] %>% 
        .[,Qgutr:=Qvillir * CLpermr / (Qvillir + CLpermr)] %>%
   # Qgut Model -- Yang et al. (2007) equation 5:
        .[,fgh_qg:=Qguth/(Qguth+ fuph.adj*cluh_gut)*Qguth/(Qguth+Qintesttransport)] %>% 
        .[,fgr_qg:=Qgutr/(Qgutr + fupr.adj*clur_gut)*Qguth/(Qguth+Qintesttransport)] %>%
   # Darwich et al. (2010) Equation 3
        .[,fah_darwichh:=1 - (1 + 0.54 * peffh)^-7] %>% 
        .[,fah_darwichr:=1 - (1 + 0.54 * peffr)^-7] %>% 
   # Darwich et al. (2010) Equation 1
        .[,fbioh:=ffph*fgh_qg*fah_darwichh] %>% 
        .[,fbior:=ffpr*fgr_qg*fah_darwichr]
   
   save(invivo.table, 
        file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))  
```   
# Add in predictions from ADMet Predictor
```{r load_admet}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

admet <- as.data.frame(read_excel(paste0(loc.wd, 
                                         "/r_data/admet/Chemicals_Caco2_export.xlsx")))
admetids <- as.data.frame(read_excel(paste0(loc.wd, 
                                         "/r_data/admet/GoodPab310forHisham.xlsx")))
admet$DTXSID <- admetids[admet[,"Identifier"],"DTXSID"]
admet$Fgut.ADMet <- signif(as.numeric(admet[,"%Fa_hum-10.0"])/100,5)
admet$Fbio.ADMet <- signif(as.numeric(admet[,"%Fb_hum-10.0"])/100,5)
invivo.table <- merge(invivo.table,
      admet[,c("DTXSID","Fgut.ADMet","Fbio.ADMet")],
      by="DTXSID",
      all.x=TRUE)

save(invivo.table, 
     file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))  
```

# Create supplemental table with all in vivo data and predictions
```{r write_suptable_invivodata}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

write.csv(invivo.table,
          file=paste0(loc.wd,"/r_data/results_for_paper/SupTableInVivoDatandPreds.csv"),
          row.names=FALSE,
          na="")
```

# Measured data from Lanevskij and Didziapetris (2019)
```{r make_caco_peff_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
      FigCacoPredPeff <- ggplot(invivo.table)+
        geom_point(aes(x = mpeff_lit, y = peffh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred. ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')),
             x = expression(bold("Measured ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')))+
    #    lims(x = c(-2,2), y = c(-2,2)) +
        scale_colour_viridis_d()+
          scale_x_log10()+
        scale_y_log10()+
        gtheme +
        theme(axis.title = element_text(size = 8)) 
print(FigCacoPredPeff)
    ggsave(FigCacoPredPeff, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredPeff.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
# Measured data from Kim et al. (2014)
```{r make_Caco_Fbio_kim_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
      FigCacoPredFbioKim <- ggplot(invivo.table)+
        geom_point(aes(y = fbioh, x = kim_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["bio,h"])),
             x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
print(FigCacoPredFbioKim)
    ggsave(FigCacoPredFbioKim, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFbioKim.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
# Measured data collected by Varma et al. (2010)
```{r make_Caco_Fabs_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
FigCacoPredFabs <- ggplot(invivo.table)+
        geom_point(aes(y = fah_darwichh, x = vo_Fa, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["abs,h"])),
             x = expression(bold("Measured")~bolditalic("F"["abs,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme 
print(FigCacoPredFabs)
    ggsave(FigCacoPredFabs, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFabs.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Evaluate Caco2 Fgut Prediction using measured data collected by Varma et al. (2010)
```{r make_Caco_Fgut_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  FigCacoPredFgut <- ggplot(invivo.table)+
        geom_point(aes(y = fgh_qg, x = vo_Fg, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Pred.")~bolditalic("F"["gut,h"])),
             x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigCacoPredFgut)
  ggsave(FigCacoPredFgut, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Evaluate ADMet Fgut Prediction using measured data collected by Varma et al. (2010)
```{r make_ADMet_Fgut_fig}
load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  FigADMetPredFgut <- ggplot(invivo.table)+
        geom_point(aes(y = Fgut.ADMet, x = vo_Fg, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("ADMet Pred.")~bolditalic("F"["gut,h"])),
             x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigADMetPredFgut)
  ggsave(FigADMetPredFgut, 
         file = paste0(loc.wd, 
                              "/r_data/results_for_paper/FigADMetPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
  
summary(lm(vo_Fg ~ Fgut.ADMet, data=invivo.table))
```

# Evaluate predicted first-pass hepatic metabolism using measured data collected by Varma et al. (2010) 
ffp=fraction first pass
```{r make_httk_Fhep_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  
  FighttkPredFhep <- ggplot(invivo.table) +
  geom_point(aes(y = ffph, x = vo_Fh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("Pred.")~bolditalic("F"["hep,h"])),
       x = expression(bold("Measured")~bolditalic("F"["hep,h"]))) +
  lims(x = c(0,1), y = c(0,1)) +
  scale_colour_viridis_d() +
  gtheme
  print(FighttkPredFhep)
  ggsave(FighttkPredFhep, file = paste0(loc.wd, "/r_data/results_for_paper/FighttkPredFhep.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
# Fbio calculated from measured data
# using first-pass metabolism only (previous httk approach)
```{r make_httk_FhepFbio_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","ffph","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","ffph","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/oldhttk-invivo-compare-fbioall.RData"))

  FigOldhttkPredFbio <- ggplot(invivo.table) +
  geom_point(aes(y = ffph, x = invivo_fbioh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("Pred.")~bolditalic("F"["hep,h"])),
       x = expression(bold("Measured")~bolditalic("F"["bio,h"]))) +
  lims(x = c(0,1), y = c(0,1)) +
  scale_colour_viridis_d() +
  gtheme
  print(FigOldhttkPredFbio)
  ggsave(FigOldhttkPredFbio, 
         file = paste0(loc.wd, "/r_data/results_for_paper/FigoldhttkPredFbio.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Fbio calculated from measured data collected by Varma et al. (2010)
```{r make_Caco_Fabs_Varma_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))    
  
  FigCacoPredFbioVarma <- ggplot(invivo.table)+
    geom_point(aes(y = fbioh, x = vo_F, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("Caco2 Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigCacoPredFbioVarma)
  ggsave(FigCacoPredFbioVarma, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFbioVarma.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Fbio estimated from rats (Wambaugh et al. (2018) Fbio)
```{r make_CacoFabsRat_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(pk_fbior) &
                          !is.na(vo_F))[,
                   c("DTXSID","Class","pk_fbior","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(pk_fbior) &
                        !is.na(kim_fbioh))[,
                 c("DTXSID","Class","pk_fbior","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/rat-human-compare-fbioall.RData"))
  
  FigCacoPredFbioRat <- ggplot(invivo.table)+
        geom_point(aes(y = invivo_fbioh, x = pk_fbior, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("Measured")~bolditalic("F"["bio,r"])),
             x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
        lims(x = c(0,1), y = c(0,1))+
        scale_colour_viridis_d()+
        gtheme
  print(FigCacoPredFbioRat)
  ggsave(FigCacoPredFbioRat, file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFbioRat.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Fbio using both Kim et al. (2014) and Varma et al. (2010)
```{r make_Caco_Fabs_All_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","fbioh","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","fbioh","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/caco2-invivo-compare-fbioall.RData"))

  FigCacoPredFbioAll <- ggplot(fbio.table)+
    geom_point(aes(y = fbioh, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("Caco2 Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigCacoPredFbioAll)
  ggsave(FigCacoPredFbioAll, 
         file = paste0(loc.wd, 
                       "/r_data/results_for_paper/FigCacoPredFbioAll.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Fbio predicted by ADMet Predictor
```{r make_admet_Fabs_fig}
  load(file=paste0(loc.wd, "/r_data/processed/caco2-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","Fbio.ADMet","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","Fbio.ADMet","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
     file=paste0(loc.wd, 
                 "/r_data/processed/admet-invivo-compare-fbioall.RData"))

  FigADMetPredFbio <- ggplot(fbio.table)+
    geom_point(aes(y = Fbio.ADMet, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("ADMet Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigADMetPredFbio)
  ggsave(FigADMetPredFbio, 
         file = paste0(loc.wd, 
                       "/r_data/results_for_paper/FigADMetPredFbio.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

# Combine the evalaution figures of the components of Fbio for the paper:
```{r multipanelfigureforpaper}
ggarrange(FigCacoPredPeff, FigCacoPredFabs, FigCacoPredFgut, FighttkPredFhep, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom")
tiff(file = paste0(loc.wd, "/r_data/results_for_paper/FigCacoPredFbioComponents.tiff"),
         height = 3*200, width = 3*200, compression = "lzw")
ggarrange(FigCacoPredPeff, FigCacoPredFabs, FigCacoPredFgut, FighttkPredFhep, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          common.legend = TRUE, legend = "bottom"+
          theme_gray(base_size = 18))
dev.off()
```
### QSPR Evaluation:

```{r caco2_qspr_pab_eval_fig}
  load(file=paste0(loc.wd, 
                   "/r_data/processed/caco2dt.RData"))

# Annotate chemical class:   
   caco2.dt$Class <- "Other"
   caco2.dt[caco2.dt$DTXSID%in%pharma$DSSTox_Substance_Id,"Class"] <-
     "Pharmaceutical"
   
      FigQSPRPredPab <- ggplot(caco2.dt)+
        geom_point(aes(x = Pab, y = Pab.Pred.Med, color=Class, shape=Class), 
                   alpha = 0.15,
                   position = position_jitter(w = 0.0, h = 0.1),
                   size=3)+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(y = expression(bold("QSPR Predicted log"["10"])*bolditalic("P"["ab"])~bold('(10'^'-6'~'cm/s)')),
             x = expression(bold("Measured log"["10"])*bolditalic("P"["ab"])~bold('(10'^'-6'~'cm/s)')))+
       # lims(x = c(-5,3), y = c(-5,3)) +
        scale_x_log10()+
        scale_y_log10()+
        scale_colour_viridis_d()+
        gtheme
  print(FigQSPRPredPab)
    ggsave(FigQSPRPredPab, file = paste0(loc.wd, 
                                         "/r_data/results_for_paper/FigQSPRPredPab.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```


Repeat all the previous figures, but use the QSPR predictions.

Load all the parameters needed to make calculations:
```{r qspr_permeability_params}
   load_honda2023(overwrite=TRUE)
   invivo.table <- gut.data
   colnames(invivo.table)[colnames(invivo.table)=="dtxsid"] <- "DTXSID"
   invivo.table <- merge(invivo.table,caco2.dt,by="DTXSID")
   invivo.table <- subset(invivo.table,DTXSID%in% chem.physical_and_invitro.data$DTXSID)
   httk.casrn <- get_cheminfo()
   
   invivo.table[,
                logP:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"logP"]]
   invivo.table[,
                MW:=chem.physical_and_invitro.data[unlist(sapply(invivo.table$DTXSID, function(x) which(x==chem.physical_and_invitro.data$DTXSID))),"MW"]]
   
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     casrn %in% httk.casrn, 
                   fuph.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Human",
                     suppress.messages = TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     casrn %in% httk.casrn, 
                   fupr.adj := parameterize_steadystate(
                     chem.cas = casrn, 
                     species = "Rat",
                     suppress.messages = TRUE,
                     default.to.human=TRUE)$Funbound.plasma,
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,cluh_us:=calc_hep_clearance(
                       chem.cas = casrn[1],
                       species = "Human", 
                       hepatic.model = "unscaled",
                       suppress.messages = TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   clur_us:=calc_hep_clearance(
                     chem.cas = casrn[1],
                     species = "Rat", 
                     hepatic.model = "unscaled",
                     suppress.messages = TRUE,
                     default.to.human=TRUE),
                   .(casrn)] 
      invivo.table[!is.na(fupr) & 
                     !is.na(clintr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffpr_us:=calc_hep_bioavailability(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(clur_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(clinth) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn,
                   ffph_us:=calc_hep_bioavailability(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages=TRUE
                     #clu=unique(cluh_us)
                     ),
                   .(casrn)]
      invivo.table[!is.na(fuph) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2ph := available_rblood2plasma(
                     species="Human",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      invivo.table[!is.na(fupr) & 
                     !is.na(logP) & 
                     !is.na(MW) & 
                     casrn %in% httk.casrn, 
                   rb2pr := available_rblood2plasma(
                     species="Rat",
                     chem.cas= casrn,
                     suppress.messages = TRUE),
                   .(casrn)]
      
  invivo.table[,cluh_hep:=cluh_us*70] %>% # L/h for 70 kg human
        .[,cluh_gut:=cluh_hep/100] %>% # approximate ratio of cyp abundances
        .[,clur_hep:=clur_us*0.25] %>% # L/h for 0.25 kg rat
        .[,clur_gut:=clur_hep/100] %>% 
        .[,ffph:=ffph_us] %>% 
        .[,ffpr:=ffpr_us]
```   
These calculations should match both the manuscript text and the code in calc_oral_bioavailability.R
```{r qspr_permeability_calcs}  

   invivo.table[,use.pab:=Pab.Pred.Med]
   invivo.table[,Pab.Type:="QSPR"]
   # peff dimensional 10-4 cm/s
   invivo.table[,peffh:=(10^(0.4926*log10(use.pab)-0.1454))] %>% 
   # Fagerholm 1996
        .[,peffr:=peffh/3.6] %>% 
   # m2 area intestine -- Yang et al. (2007)
        .[,Asmallintestineh:=0.66] %>% 
        .[,Asmallintestiner:=71/(100^2)] %>%
   # permeability clearance (CLperm) Yang et al. (2007) equation 8:
   # 10^-4 cm / s * m2 * 1000 L / m^3 / 10^4 * 1 m / 100 cm * 3600 s / h = L / h
        .[,CLpermh :=peffh * Asmallintestineh * 1000/10^4/100*3600] %>% 
        .[,CLpermr :=peffr * Asmallintestiner * 1000/10^4/100*3600] %>% 
   # Yang et al. (2007) value of 18 L/h blood flow to microvilli of intestinal lumen
        .[,Qvillih:=18] %>% 
        .[,Qvillir:=0.65] %>%
   # Qgut "in terms of fundamental parameters" -- Yang et al. (2007) equation 6:
        .[,Qguth:=Qvillih * CLpermh / (Qvillih + CLpermh)] %>% 
        .[,Qgutr:=Qvillir * CLpermr / (Qvillir + CLpermr)] %>%
   # Qgut Model -- Yang et al. (2007) equation 5:
        .[,fgh_qg:=Qguth/(Qguth+ fuph.adj*cluh_gut)*Qguth/(Qguth+Qintesttransport)] %>% 
        .[,fgr_qg:=Qgutr/(Qgutr + fupr.adj*clur_gut)*Qguth/(Qguth+Qintesttransport)] %>%
   # Darwich et al. (2010) Equation 3
        .[,fah_darwichh:=1 - (1 + 0.54 * peffh)^-7] %>% 
        .[,fah_darwichr:=1 - (1 + 0.54 * peffr)^-7] %>% 
   # Darwich et al. (2010) Equation 1
        .[,fbioh:=ffph*fgh_qg*fah_darwichh] %>% 
        .[,fbior:=ffpr*fgr_qg*fah_darwichr]
  
  save(invivo.table, file=paste0(loc.wd, 
                                 "/r_data/processed/qspr-invivo-compare2.RData"))    
```   
   
```{r make_qspr_peff_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredPeff <- ggplot(invivo.table)+
    geom_point(aes(x = mpeff_lit, y = peffh, color=Class, shape=Class), 
                alpha = 0.75,
                size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')),
         x = expression(bold("Measured ")*bolditalic("P"["eff,h"])~bold('(10'^'-4'~'cm/s)')))+
    scale_colour_viridis_d()+
    scale_x_log10()+
    scale_y_log10()+
    gtheme +
    theme(axis.title = element_text(size = 8)) 
  print(FigQSPRPredPeff)
  ggsave(FigQSPRPredPeff, file = 
           paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredPeff.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
```{r make_QSPR_Fbio_kim_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFbioKim <- ggplot(invivo.table)+
  geom_point(aes(y = fbioh, x = kim_fbioh, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3) +
  geom_abline(slope = 1, linetype = "dashed") +
  labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
       x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
  lims(x = c(0,1), y = c(0,1))+
  scale_colour_viridis_d()+
  gtheme
  print(FigQSPRPredFbioKim)
  ggsave(FigQSPRPredFbioKim, file = 
           paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredFbioKim.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fabs_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFabs <- ggplot(invivo.table) +
    geom_point(aes(y = fah_darwichh, x = vo_Fa, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3) +
    geom_abline(slope = 1, linetype = "dashed") +
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["abs,h"])),
         x = expression(bold("Measured")~bolditalic("F"["abs,h"]))) +
    lims(x = c(0,1), y = c(0,1)) +
    scale_colour_viridis_d() +
    gtheme 

  print(FigQSPRPredFabs)
  ggsave(FigQSPRPredFabs, file = 
           paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredFabs.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fgut_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))
  
  FigQSPRPredFgut <- ggplot(invivo.table)+
  geom_point(aes(y = fgh_qg, x = vo_Fg, color=Class, shape=Class), 
                 alpha = 0.75,
                 size=3)+
  geom_abline(slope = 1, linetype = "dashed")+
  labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["gut,h"])),
       x = expression(bold("Measured")~bolditalic("F"["gut,h"])))+
  lims(x = c(0,1), y = c(0,1))+
  scale_colour_viridis_d()+
  gtheme
  print(FigQSPRPredFgut)
  
  ggsave(FigQSPRPredFgut, file = 
           paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredFgut.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fhep_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  FigQSPRPredFhep <- ggplot(invivo.table)+
    geom_point(aes(y = ffph, x = vo_Fh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3) +
    geom_abline(slope = 1, linetype = "dashed") +
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["hep,h"])),
         x = expression(bold("Measured")~bolditalic("F"["hep,h"]))) +
    lims(x = c(0,1), y = c(0,1)) +
    scale_colour_viridis_d() +
    gtheme
  print(FigQSPRPredFhep)
  ggsave(FigQSPRPredFhep, file = 
           paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredFhep.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```

```{r make_QSPR_Fbio_Varma_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))
  
  FigQSPRPredFbioVarma <- ggplot(invivo.table)+
    geom_point(aes(y = fbioh, x = vo_F, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigQSPRPredFbioVarma)
  ggsave(FigQSPRPredFbioVarma, 
         file = paste0(loc.wd, 
                       "/r_data/results_for_paper/FigQSPRPredFbioVarma.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
# Fbio using both Kim et al. (2014) and Varma et al. (2010)
```{r make_QSPR_Fbio_all_fig}
  load(file=paste0(loc.wd, "/r_data/processed/qspr-invivo-compare2.RData"))

  varma.chems <- subset(invivo.table,!is.na(vo_F))[,
                   c("DTXSID","Class","fbioh","vo_F")]
  kim.chems <- subset(invivo.table,!is.na(kim_fbioh))[,
                 c("DTXSID","Class","fbioh","kim_fbioh")]
  colnames(varma.chems)[4] <- "invivo_fbioh"
  colnames(kim.chems)[4] <- "invivo_fbioh"
  varma.chems$Reference <- "Varma2010"
  kim.chems$Reference <- "Kim2014"
  fbio.table <- rbind(varma.chems,kim.chems)
  invivo.table <- fbio.table
  save(invivo.table,
       file=paste0(loc.wd, 
                   "/r_data/processed/qspr-invivo-compare-fbioall.RData"))

  FigQSPRPredFbioAll <- ggplot(fbio.table)+
    geom_point(aes(y = fbioh, x = invivo_fbioh, color=Class, shape=Class), 
                   alpha = 0.75,
                   size=3)+
    geom_abline(slope = 1, linetype = "dashed")+
    labs(y = expression(bold("QSPR Predicted")~bolditalic("F"["bio,h"])),
         x = expression(bold("Measured")~bolditalic("F"["bio,h"])))+
    lims(x = c(0,1), y = c(0,1))+
    scale_colour_viridis_d()+
    gtheme
  print(FigQSPRPredFbioAll)
  ggsave(FigQSPRPredFbioAll, file = 
         paste0(loc.wd, "/r_data/results_for_paper/FigQSPRPredFbioAll.tiff"),
         height = 3, width = 3, dpi = 600, compression = "lzw")
```
### Evaluation Statistics
We made new versions of "invivo.table" combining the Fbio data from Varma and Kim
and saved them in different RData files
```{r eval_table}
evaluations <- data.frame()
evaluations["Peff",c("In Vivo","Predicted","Reference","Data")] <- 
  c("mpeff_lit","peffh","Lanevskij and Didziapetris (2019)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fabs",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fa","fah_darwichh","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fgut-QGutModel",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fg","fgh_qg","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fgut-ADMet",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fg","Fgut.ADMet","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fhep",c("In Vivo","Predicted","Reference","Data")] <- 
  c("vo_Fh","ffph","Varma et al. (2010)",
    "/r_data/processed/caco2-invivo-compare2.RData")
evaluations["Fbio",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","fbioh","Kim et al. (2014)",
    "/r_data/processed/caco2-invivo-compare-fbioall.RData")
evaluations["Fbio-Rat",c("In Vivo","Predicted","Reference","Data")] <- 
  c("kim_fbioh","pk_fbior","Wambaugh et al. (2018)",
    "/r_data/processed/all_gut_data_invivotable.RData")
evaluations["Fbio-QSPR",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","fbioh","Kim et al. (2014)",
    "/r_data/processed/qspr-invivo-compare-fbioall.RData")
evaluations["Fbio-ADMet",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","Fbio.ADMet","Kim et al. (2014)",
    "/r_data/processed/admet-invivo-compare-fbioall.RData")
evaluations["Fbio-PreviousHTTK",c("In Vivo","Predicted","Reference","Data")] <- 
  c("invivo_fbioh","ffph","Kim et al. (2014)",
    "/r_data/processed/oldhttk-invivo-compare-fbioall.RData")

eval.table <- data.frame()
for (this.evaluation in row.names(evaluations))
{
# Load the relevant invivo.table RData
  load(file=paste0(loc.wd, evaluations[this.evaluation,"Data"]))
# Restrict to only non-NA values:
  invivo.table <- as.data.frame(invivo.table)
  this.data <- subset(invivo.table,
                      !is.na(invivo.table[, evaluations[this.evaluation,"In Vivo"]]) &
                      !is.na(invivo.table[, evaluations[this.evaluation,"Predicted"]]))
  num.chem <- dim(this.data)[1]
  this.fit <- lm(this.data[, evaluations[this.evaluation,"In Vivo"]] ~
                 this.data[, evaluations[this.evaluation,"Predicted"]])
  R2 <- summary(this.fit)$adj.r.squared
  p.value <- summary(this.fit)$coefficients[2,4]
  RMSE <- sqrt(mean((this.data[, evaluations[this.evaluation,"In Vivo"]]  -
                     this.data[, evaluations[this.evaluation,"Predicted"]])^2))
  eval.table[this.evaluation,c("N.Chem","Reference","R2","p.Value","RMSE")] <- c(
    num.chem,
    evaluations[this.evaluation,"Reference"],
    signif(R2,2),
    signif(p.value,2),
    signif(RMSE,3)
  )
}
knitr::kable(eval.table, 
             caption = "Evaluation of predictions against in vivo data for Fbio and contributing factors.",
             floating.environment="sidewaystable") 
write.csv(eval.table,file=paste0(loc.wd,"/r_data/results_for_paper/Tableinvivoevaluationsummary.csv"))
```
