---
title: "Honda et al. (unsubmitted): Analysis and Figure Generation"
author: "Greg Honda"
date: "August 3, 2020"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Honda et al. (unsubmitted): Analysis and Figure Generation}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---
wambaugh.john@epa.gov

## Abstract
Apical-to-basolateral (PAB) and basolateral-to-apical (PBA) measurements were 
made in the Caco-2 assay for 484 environmental and pharmaceutical chemicals. 
After filtering, 310 chemicals had a useable PAB and 396 had a useable PBA. 
Replicates (> 30) were measured for the control chemicals Warfarin, Talinolol, 
and Ranitidine. Measurement uncertainty was high (SD: 0.3 log10 units) for the 
low permeability control (Ranitidine). Of our measured PAB, > 80% had high PAB 
(> 10x10-6 cm/s). Our measured PAB were combined with literature values to 
develop a classification quantitative-structure-property relationship (QSPR) 
model, with a balanced accuracy of 80% for the test set. Measured PAB were also 
used to predict in vivo oral bioavailability (Fbio,h)in human for 
pharmaceuticals, and performed slightly better (R2: -0.03, RMSE: 0.30) than 
assuming a fixed value for PAB. Additionally, measured PAB were used for 
prediction of in vivo oral bioavailability in rat, which resulted in improved 
prediction of maximum concentration (previous R2: 0.32, updated R2: 0.70). 
Finally, measurement uncertainty was accounted for in estimates of 
oral-equivalent dose (OED) from ToxCast in vitro assays for a simulated 
population using a Monte-Carlo method. OED were subsequently compared with 
exposure estimates, and the influence of different extrapolation assumptions 
on the bioactivity-to-exposure ratio (BER) was evaluated. Generally, the large 
measurement uncertainty for low PAB makes the use of Caco-2 data for accurate 
prediction of point values difficult. However, accounting for uncertainty 
enables the upper limits for oral bioavailability to be accurately represented 
in calculation of OED.

## Prepare for session

### Clear memory
```{r setup}
# Delete all objects from memory:
rm(list=ls())
```

### Set the figure size
```{r knitr_setup}
loc.wd <- "C:/Users/jwambaug/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Research Projects/Caco2/Honda_Caco2"
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4)
knitr::opts_knit$set(root.dir = loc.wd)
```

### Load the relevant libraries
```{r r_setup}

packages <- c("ggplot2","hexbin","dplyr","gplots","httk","RColorBrewer",
        "viridis","data.table","magrittr","readxl",
        "stringr","gridExtra","stringi","RMySQL","DBI","grid","xlsx","lattice",
        "gtable","ggpubr","randomForest","caret","recipes","quantregForest",
        "tcpl","scales")
sapply(packages, require,character.only=TRUE) #Note, the "character.only" argument is necessary her
```

### Load custom scripts for analysis
```{r load_useful_scripts}
source(paste0(loc.wd,"/r_scripts/Honda_caco2_utilities.R"))
#source('C:/Users/GHONDA/Documents/HTTKOralRoute/gh_ionization_functions.R')
#source("C:/Users/GHONDA/Documents/R homebrew/chemprop_connect/query_dsstox.measchemprop.R")
#source(paste0(loc.wd,"/r_scripts/rf_train.R"))
#source(paste0(loc.wd,"/r_scripts/Honda_caco2_fullmodel.R"))


```

## ANALYSIS

Configure figure theme
```{r summary}
low_rec_co <- 0.4
high_rec_co <- 2
gtheme <- theme(axis.title = element_text(size=12,color="black",face="bold"),
                axis.text.y = element_text(size=10, color = "black",face="bold"),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 10),
                legend.key.size = unit(10, "points"),
                panel.background = element_rect(fill="white"),
                axis.line = element_line(color="black"),
                axis.ticks.y = element_line(color="black"),
                legend.position = "top",
                axis.line.x=element_line(color="black"),
                axis.ticks.x=element_line(color="black"),
                axis.text.x = element_text(size = 10,face="bold",color="black"),
                plot.title = element_text(hjust=0,size=12,face="bold"))
```

## Comparison with Cvt Data
Omitted for now because we can't predict rat bioavailability

```{r cvt_compare, eval=FALSE}
    #gcl <- marrangeGrob(grobs=list(gcl1,gcl2,gcl3,gcl4),ncol=2,nrow=2,top=NULL)
    #ggsave(gcl,file=paste0(loc.wd,"/r_data/figures/05FEB2019/ffp.png"),dpi=600,height=9,width=9)
    
    load(paste0(loc.wd,"/r_data/tk_data/PKstats-2018-01-16.RData"))
    pkstats2 <- as.data.table(copy(PKstats)) %>% 
      .[Route == "po", Route := "Oral"] %>% 
      .[Route == "iv", Route := "IV"] %>% 
      .[, Route := factor(Route, levels = c("Oral", "IV"))]
    
    ratpk.dt <- copy(pkstats2)
    
    pred.all <- allgut.casrn2[!is.na(dtxsid)][fbio.calc.dt, on = "dtxsid"]
    
    {
      
      pkcomp.dt <- pred.all[pab.use == "default_1.6",][,.("CAS" = casrn, 
                              "fbior_default" = fbior, 
                              "fabsr_default" = fah_darwich,
                              "fgutr_default" = fgr_qg,
                              "fhepr_default" = ffpr)][ratpk.dt, on= "CAS"] %>% 
        .[, AUC_default := AUC.pred] %>% 
        .[Route == "Oral", AUC_default := AUC.pred*fbior_default] %>% 
        .[, Cmax_default := Cmax.pred] %>% 
        .[Route == "Oral", Cmax_default := Cmax.pred*fbior_default] %>% 
        .[, ]
      
      pkcomp.dt <- pred.all[pab.use == "rf_q50",][,.("CAS" = casrn, 
                                                          "fbior_rfq50" = fbior, 
                                                          "fabsr_rfq50" = fah_darwich,
                                                          "fgutr_rfq50" = fgr_qg,
                                                          "fhepr_rfq50" = ffpr)][pkcomp.dt, on= "CAS"] %>% 
        .[, AUC_rfq50 := AUC.pred] %>% 
        .[Route == "Oral", AUC_rfq50 := AUC.pred*fbior_rfq50] %>% 
        .[, Cmax_rfq50 := Cmax.pred] %>% 
        .[Route == "Oral", Cmax_rfq50 := Cmax.pred*fbior_rfq50] %>% 
        .[, ]
      
      pkcomp.dt <- pred.all[pab.use == "mpab",][,.("CAS" = casrn, 
                                                   "fbior_mpab" = fbior, 
                                                   "fabsr_mpab" = fah_darwich,
                                                   "fgutr_mpab" = fgr_qg,
                                                   "fhepr_mpab" = ffpr)][pkcomp.dt, on= "CAS"] %>% 
        .[, AUC_mpab := AUC.pred] %>% 
        .[Route == "Oral", AUC_mpab := AUC.pred*fbior_mpab] %>% 
        .[, Cmax_mpab := Cmax.pred] %>% 
        .[Route == "Oral", Cmax_mpab := Cmax.pred*fbior_mpab] %>% 
        .[, ]
      
      pkcomp.dt <- pred.all[pab.use == "rf_cat.val",][,.("CAS" = casrn, 
                                                   "fbior_rfcat" = fbior, 
                                                   "fabsr_rfcat" = fah_darwich,
                                                   "fgutr_rfcat" = fgr_qg,
                                                   "fhepr_rfcat" = ffpr)][pkcomp.dt, on= "CAS"] %>% 
        .[, AUC_rfcat := AUC.pred] %>% 
        .[Route == "Oral", AUC_rfcat := AUC.pred*fbior_rfcat] %>% 
        .[, Cmax_rfcat := Cmax.pred] %>% 
        .[Route == "Oral", Cmax_rfcat := Cmax.pred*fbior_rfcat]
      
      pkcomp.dt[, AUC_fhep := AUC.pred] %>% 
        .[Route == "Oral", AUC_fhep := AUC.pred*fhepr_default] %>% 
        .[, Cmax_fhep := Cmax.pred] %>% 
        .[Route == "Oral", Cmax_fhep := Cmax.pred*fhepr_default]
      
      fbiorcomp.dt <- unique(pkcomp.dt[,.(CAS, Fbio, fbior_default, fbior_mpab, fbior_rfcat, fbior_rfq50, fhepr_default)])

      
     
      fbior.res <- rbind(rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = Fbio, ycalc = fbior_mpab)][,"route" := "Oral"],
                    pkcomp.dt[Route == "IV", xysummary(ymeas = Fbio, ycalc = fbior_mpab)][,"route" := "IV"],
                    pkcomp.dt[, xysummary(ymeas = Fbio, ycalc = fbior_mpab)][,"route" := "All"])[,"method" := "mpab"],
              rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = Fbio, ycalc = fbior_default)][,"route" := "Oral"],
                    pkcomp.dt[Route == "IV", xysummary(ymeas = Fbio, ycalc = fbior_default)][,"route" := "IV"],
                    pkcomp.dt[, xysummary(ymeas = Fbio, ycalc = fbior_default)][,"route" := "All"])[,"method" := "default"],
              rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = Fbio, ycalc = fbior_rfcat)][,"route" := "Oral"],
                    pkcomp.dt[Route == "IV", xysummary(ymeas = Fbio, ycalc = fbior_rfcat)][,"route" := "IV"],
                    pkcomp.dt[, xysummary(ymeas = Fbio, ycalc = fbior_rfcat)][,"route" := "All"])[,"method" := "rfcat"],
              rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = Fbio, ycalc = fbior_rfq50)][,"route" := "Oral"],
                    pkcomp.dt[Route == "IV", xysummary(ymeas = Fbio, ycalc = fbior_rfq50)][,"route" := "IV"],
                    pkcomp.dt[, xysummary(ymeas = Fbio, ycalc = fbior_rfq50)][,"route" := "All"])[,"method" := "rfq50"],
              rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = Fbio, ycalc = fhepr_default)][,"route" := "Oral"],
                    pkcomp.dt[Route == "IV", xysummary(ymeas = Fbio, ycalc = fhepr_default)][,"route" := "IV"],
                    pkcomp.dt[, xysummary(ymeas = Fbio, ycalc = fhepr_default)][,"route" := "All"])[,"method" := "fhep"])[, "measure" := "Fbior"]
        
      auc.res <- rbind(rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred))][,"route" := "All"])[,"method" := "none"],
                  rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred.Fbio))][,"route" := "Oral"],
                        pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred.Fbio))][,"route" := "IV"],
                        pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC.pred.Fbio))][,"route" := "All"])[,"method" := "Fbio_meas"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_mpab))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_mpab))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC_mpab))][,"route" := "All"])[,"method" := "mpab"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_default))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_default))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC_default))][,"route" := "All"])[,"method" := "default"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfcat))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfcat))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfcat))][,"route" := "All"])[,"method" := "rfcat"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfq50))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfq50))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC_rfq50))][,"route" := "All"])[,"method" := "rfq50"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_fhep))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(AUC), ycalc = log10(AUC_fhep))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(AUC), ycalc = log10(AUC_fhep))][,"route" := "All"])[,"method" := "fhep"])[, "measure" := "log10AUC"]
      
      cmax.res <- rbind(rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred))][,"route" := "All"])[,"method" := "none"],
                  rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred.Fbio))][,"route" := "Oral"],
                        pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred.Fbio))][,"route" := "IV"],
                        pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred.Fbio))][,"route" := "All"])[,"method" := "Fbio_meas"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_mpab))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_mpab))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_mpab))][,"route" := "All"])[,"method" := "mpab"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_default))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_default))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_default))][,"route" := "All"])[,"method" := "default"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfcat))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfcat))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfcat))][,"route" := "All"])[,"method" := "rfcat"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfq50))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfq50))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_rfq50))][,"route" := "All"])[,"method" := "rfq50"],
            rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_fhep))][,"route" := "Oral"],
                  pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_fhep))][,"route" := "IV"],
                  pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax_fhep))][,"route" := "All"])[,"method" := "fhep"])[, "measure" := "log10Cmax"]
      
      
      write.xlsx(fbior.res, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/rat_tk.xlsx"), append = FALSE, sheetName = "fbior")
      write.xlsx(auc.res, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/rat_tk.xlsx"), append = TRUE, sheetName = "AUC")
      write.xlsx(cmax.res, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/rat_tk.xlsx"), append = TRUE, sheetName = "Cmax")
      comb.res <- rbind(fbior.res, auc.res, cmax.res)
      write.xlsx(comb.res, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/rat_tk.xlsx"), append = TRUE, sheetName = "collected")
      comb.res2 <- melt(comb.res[,.(measure, method, route, xyr2, xyrmse, xycor, xyN = as.numeric(xyN))], measure.vars = c("xyr2", "xyrmse", "xycor", "xyN"), value.name = "val")
      comb.res3 <- dcast(comb.res2, route + measure + variable ~ method, value.var = "val")
      write.xlsx(comb.res3, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/rat_tk.xlsx"), append = TRUE, sheetName = "collected_pivot")
      
      
      # rbind(pkcomp.dt[Route == "Oral", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred))][,"route" := "Oral"],
      #       pkcomp.dt[Route == "IV", xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred))][,"route" := "IV"],
      #       pkcomp.dt[, xysummary(ymeas = log10(Cmax), ycalc = log10(Cmax.pred.new))][,"route" := "All"])[,"measure" := "log10Cmax"]
      # 
      leg.fig <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_mpab), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        lims(x = c(-4,4), y = c(-4,4))+
        theme(legend.position = "bottom")+
        annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      gleg <- get_legend(leg.fig)
      select_grobs <- function(lay) {
        id <- unique(c(t(lay))) 
        id[!is.na(id)]
      } 
      hlay1 <- rbind(c(1,2,3),
                     c(1,2,3),
                     c(1,2,3),
                     c(1,2,3),
                     c(1,2,3),
                     c(4,4,4))
      hlay2 <- rbind(c(1,2,3,4),
                     c(1,2,3,4),
                     c(1,2,3,4),
                     c(1,2,3,4),
                     c(1,2,3,4),
                     c(5,5,5,5))
      
      
      {
      g2a <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC.pred), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
          theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "a)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      g2b <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC.pred.Fbio), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "b)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      g2c <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_mpab), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      gs2a <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_fhep), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "a)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      gs2b <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_default), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "b)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      gs2c <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_rfcat), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "d)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      gs2d <- ggplot(pkcomp.dt)+
        geom_point(aes(x = log10(AUC), y= log10(AUC_rfq50), color = Route))+
        geom_abline(slope = 1, linetype = "dashed")+
        labs(title = "",
             x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
             y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
        theme_bw()+
        gtheme+
        theme(legend.position = "none")+
        lims(x = c(-4,4), y = c(-4,4))+
        annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                          ymin = 3.5, ymax = 3.5, xmin = -4, xmax = -4)
      
      
      g2 <- marrangeGrob(grobs = list(g2a, g2b, g2c, gs2c, gleg), nrow = 2, ncol = 3, layout_matrix = hlay2, top = NULL)
      ggsave(g2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/AUC_3x.tiff"), 
             dpi = 600, width = 9, height = 4, compression = "lzw")
      gs2 <- marrangeGrob(grobs = list(gs2a, gs2b, gs2d,gleg), nrow = 2, ncol = 3, layout_matrix = hlay1, top = NULL)
      ggsave(gs2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/sAUC_4x.tiff"), 
             dpi = 600, width = 12, height = 4, compression = "lzw")
      
      }
      
      {
        auc.dt <- rbind(pkcomp.dt[,.(x = AUC, y = AUC.pred, Route)][,"col.nm" := 1],
                        pkcomp.dt[,.(x = AUC, y = AUC.pred.Fbio, Route)][,"col.nm" := 2],
                        pkcomp.dt[,.(x = AUC, y = AUC_mpab, Route)][,"col.nm" := 3],
                        pkcomp.dt[,.(x = AUC, y = AUC_rfcat, Route)][,"col.nm" := 4]
        )
        txt.dt <- data.table(col.nm = 1:4, y = 3.5, x = -3.5, labl = paste0("bold('",c("a","b","c","d"),")')"))
        
        g2 <- ggplot(auc.dt)+
          facet_grid(~col.nm)+
          geom_point(aes(x = log10(x), y = log10(y), color = Route))+
          geom_text(data = txt.dt, aes(x = x, y = y, label = labl), hjust = 0, parse = T)+
          geom_abline(slope = 1, linetype = "dashed")+
          lims(x = c(-4,4), y = c(-4,4))+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
          coord_equal()+
          theme_bw()+
          gtheme+
          theme(strip.background = element_rect(fill = NA, color = NA),
                strip.text = element_blank(),
                legend.position = "bottom")
        
        auc.dt <- rbind(pkcomp.dt[,.(x = AUC, y = AUC_fhep, Route)][,"col.nm" := 1],
                        pkcomp.dt[,.(x = AUC, y = AUC_default, Route)][,"col.nm" := 2],
                        pkcomp.dt[,.(x = AUC, y = AUC_rfq50, Route)][,"col.nm" := 3]
        )
        txt.dt <- data.table(col.nm = 1:3, y = 3.5, x = -3.5, labl = paste0("bold('",c("a","b","c"),")')"))
        
        gs2 <- ggplot(auc.dt)+
          facet_grid(~col.nm)+
          geom_point(aes(x = log10(x), y = log10(y), color = Route))+
          geom_text(data = txt.dt, aes(x = x, y = y, label = labl), hjust = 0, parse = T)+
          geom_abline(slope = 1, linetype = "dashed")+
          lims(x = c(-4,4), y = c(-4,4))+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"AUC (mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"AUC (mg*h/L)")))+
          coord_equal()+
          theme_bw()+
          gtheme+
          theme(strip.background = element_rect(fill = NA, color = NA),
                strip.text = element_blank(),
                legend.position = "bottom")
        
        ggsave(g2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/AUC_4x.tiff"), 
               dpi = 600, width = 9, height = 4, compression = "lzw")
        ggsave(gs2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/sAUC_3x.tiff"), 
               dpi = 600, width = 9, height = 4, compression = "lzw")
        
        cmax.dt <- rbind(pkcomp.dt[,.(x = Cmax, y = Cmax.pred, Route)][,"col.nm" := 1],
                        pkcomp.dt[,.(x = Cmax, y = Cmax.pred.Fbio, Route)][,"col.nm" := 2],
                        pkcomp.dt[,.(x = Cmax, y = Cmax_mpab, Route)][,"col.nm" := 3],
                        pkcomp.dt[,.(x = Cmax, y = Cmax_rfcat, Route)][,"col.nm" := 4]
        )
        txt.dt <- data.table(col.nm = 1:4, y = 2, x = -3.5, labl = paste0("bold('",c("a","b","c","d"),")')"))
        
        g3 <- ggplot(cmax.dt)+
          facet_grid(~col.nm)+
          geom_point(aes(x = log10(x), y = log10(y), color = Route))+
          geom_text(data = txt.dt, aes(x = x, y = y, label = labl), hjust = 0, parse = T)+
          geom_abline(slope = 1, linetype = "dashed")+
          lims(x = c(-4,3), y = c(-4,3))+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*bolditalic("C"["max"])~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*bolditalic("C"["max"])~"(mg*h/L)")))+
          coord_equal()+
          theme_bw()+
          gtheme+
          theme(strip.background = element_rect(fill = NA, color = NA),
                strip.text = element_blank(),
                legend.position = "bottom")
        
        cmax.dt <- rbind(pkcomp.dt[,.(x = Cmax, y = Cmax_fhep, Route)][,"col.nm" := 1],
                        pkcomp.dt[,.(x = Cmax, y = Cmax_default, Route)][,"col.nm" := 2],
                        pkcomp.dt[,.(x = Cmax, y = Cmax_rfq50, Route)][,"col.nm" := 3]
        )
        txt.dt <- data.table(col.nm = 1:3, y = 2, x = -3.5, labl = paste0("bold('",c("a","b","c"),")')"))
        
        gs3 <- ggplot(cmax.dt)+
          facet_grid(~col.nm)+
          geom_point(aes(x = log10(x), y = log10(y), color = Route))+
          geom_text(data = txt.dt, aes(x = x, y = y, label = labl), hjust = 0, parse = T)+
          geom_abline(slope = 1, linetype = "dashed")+
          lims(x = c(-4,3), y = c(-4,3))+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*bolditalic("C"["max"])~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*bolditalic("C"["max"])~"(mg*h/L)")))+
          coord_equal()+
          theme_bw()+
          gtheme+
          theme(strip.background = element_rect(fill = NA, color = NA),
                strip.text = element_blank(),
                legend.position = "bottom")
        
        ggsave(g3, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/Cmax_4x.tiff"), 
               dpi = 600, width = 9, height = 4, compression = "lzw")
        ggsave(gs3, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/sCmax_3x.tiff"), 
               dpi = 600, width = 9, height = 4, compression = "lzw")
      
      
      }
        
        
      {
        g2a <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax.pred), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "a)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        g2b <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax.pred.Fbio), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "b)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        g2c <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax_mpab), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2a <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax_fhep), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "a)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2b <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax_default), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "b)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2c <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax_rfcat), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2d <- ggplot(pkcomp.dt)+
          geom_point(aes(x = log10(Cmax), y= log10(Cmax_rfq50), color = Route))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured log"["10"]*"C"["max"]~"(mg*h/L)")),
               y = expression(bold("Predicted log"["10"]*"C"["max"]~"(mg*h/L)")))+
          theme_bw()+
          gtheme+
          theme(legend.position = "none")+
          lims(x = c(-4,3), y = c(-4,3))+
          annotation_custom(grob = text_grob(label = "d)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        
        g2 <- marrangeGrob(grobs = list(g2a, g2b, g2c, gleg), nrow = 2, ncol = 3, layout_matrix = hlay1, top = NULL)
        ggsave(g2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/Cmax_3x.tiff"), 
               dpi = 600, width = 9, height = 4, compression = "lzw")
        gs2 <- marrangeGrob(grobs = list(gs2a, gs2b, gs2c,gs2d,gleg), nrow = 2, ncol = 3, layout_matrix = hlay2, top = NULL)
        ggsave(gs2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/sCmax_4x.tiff"), 
               dpi = 600, width = 12, height = 4, compression = "lzw")
      }
      
      {
        
        g2 <- ggplot(pkcomp.dt)+
          geom_point(aes(x = Fbio, y= (fbior_mpab)))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured ")*bolditalic("F"["bio,r"])),
               y = expression(bold("Predicted ")*bolditalic("F"["bio,r"])))+
          theme_bw()+
          gtheme+
          lims(x = c(0,1), y = c(0,1))
        
        gs2a <- ggplot(pkcomp.dt)+
          geom_point(aes(x = Fbio, y= (fhepr_default)))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured ")*bolditalic("F"["bio,r"])),
               y = expression(bold("Predicted ")*bolditalic("F"["hep,r"])))+
          theme_bw()+
          gtheme+
          lims(x = c(0,1), y = c(0,1))+
          annotation_custom(grob = text_grob(label = "a)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2b <- ggplot(pkcomp.dt)+
          geom_point(aes(x = Fbio, y= (fbior_default)))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured ")*bolditalic("F"["bio,r"])),
               y = expression(bold("Predicted ")*bolditalic("F"["bio,r"])))+
          theme_bw()+
          gtheme+
          lims(x = c(0,1), y = c(0,1))+
          annotation_custom(grob = text_grob(label = "b)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2c <- ggplot(pkcomp.dt)+
          geom_point(aes(x = Fbio, y= (fbior_rfcat)))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured ")*bolditalic("F"["bio,r"])),
               y = expression(bold("Predicted ")*bolditalic("F"["bio,r"])))+
          theme_bw()+
          gtheme+
          lims(x = c(0,1), y = c(0,1))+
          annotation_custom(grob = text_grob(label = "c)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        gs2d <- ggplot(pkcomp.dt)+
          geom_point(aes(x = Fbio, y= (fbior_rfq50)))+
          geom_abline(slope = 1, linetype = "dashed")+
          labs(title = "",
               x = expression(bold("Measured ")*bolditalic("F"["bio,r"])),
               y = expression(bold("Predicted ")*bolditalic("F"["bio,r"])))+
          theme_bw()+
          gtheme+
          lims(x = c(0,1), y = c(0,1))+
          annotation_custom(grob = text_grob(label = "d)", face = "bold", hjust = 0), 
                            ymin = 2.5, ymax = 2.5, xmin = -4, xmax = -4)
        
        ggsave(g2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/Fbior_1x.tiff"), 
               dpi = 600, width = 4, height = 4, compression = "lzw")
        gs2 <- marrangeGrob(grobs = list(gs2a, gs2b, gs2c,gs2d), nrow = 1, ncol = 4, top = NULL)
        ggsave(gs2, file = paste0(loc.wd, "/r_data/results_for_paper/rat_tk/Fbior_4x.tiff"), 
               dpi = 600, width = 12, height = 3, compression = "lzw")
      }
      
    }
  
```
